### 2017-05-11 cpsviams.tex
CPS talk notes.

\title{Covariant Phase Space via MultiSymplectic Geometry}
\author{
        Antonio Michele Miti \\
                Department of Mathematics and Physics\\
        Università Cattolica del Sacro Cuore\\
        via Musei X, Brescia xxx, \underline{Italy}
}
\date{\today}

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage[diffgeo]{../Math-Symbols-List/commonmathsymb}

\begin{document}
\maketitle

\begin{abstract}
This is the paper's abstract \ldots
\end{abstract}

\section{Introduction: multisymplectic landscape at glance}
Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.

\begin{figure}

\end{figure}

\begin{itemize}
 \item the starting point is the \emph{configuration bundle} 
 	\begin{displaymath}
 		E = \left( \pi_{M,E} : E\rightarrow M \right)
 	\end{displaymath}
 	the object encoding the kinematics.
 \item from that we have constructed the \emph{I jet bundle} applying the jet functor to $E$ 
 	\begin{displaymath}
 	J^1E = \left( \pi_{J^1 M,E} : J^1 M\rightarrow M \right)
 	\end{displaymath} 
 	that is an affine bundle over $E$.
 \item Then, we considered other two vector bundle derived from the first jet:
 	\begin{displaymath}
 	J^{1 \TwistedAffine}E = \left( \pi_{J^{1 \TwistedAffine} M,E} : J^{1 \TwistedAffine} M\rightarrow M \right)
 	\end{displaymath}
	twisted affine dual of $J^1E$ called \emph{"extended multiphase space"}.
	\begin{displaymath}
	\vec{J}^{1 \TwistedLinear}E = \left( \pi_{J^{1 \TwistedLinear} M,E} : J^{1 \TwistedLinear} M\rightarrow M \right)
	\end{displaymath}
	twisted linear dual of $J^1 E$ called \emph{"standard multiphase space"}. \footnote{It can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}
	The first one can be also seen as an affine line bundle over the second one.

\end{itemize}

\paragraph{Outline}
The remainder of this article is organized as follows.
Section~\ref{previous work} gives account of previous work.
Our new and exciting results are described in Section~\ref{results}.
Finally, Section~\ref{conclusions} gives the conclusions.

\section{Previous work}\label{previous work}
A much longer \LaTeXe{} example was written by Gil~\cite{Gil:02}.

\section{Results}\label{results}
In this section we describe the results.

\section{Conclusions}\label{conclusions}
We worked hard, and achieved very little.

%\bibliographystyle{abbrv}
%\bibliography{main}

\end{document}

### 2017-05-11 ms-sigmaconstruction.tex
CPS talk notes.

% Geometric Fields Mechanics: Sigma Construction
% Author: Antonio miti

\documentclass[border=10pt]{standalone}
\usepackage{tikz}

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},
   tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},
      tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},               
   verticalsmall/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},
   verticalbig/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1cm, minimum height=1cm,
                  text centered, font=\sffamily},                              
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

\begin{document}

% Drawing part, node distance is 1.5 cm and every node
% is prefilled with white background

\begin{tikzpicture}[node distance=2.25cm,
    every node/.style={fill=white, font=\sffamily}, align=center]

  % Specification of nodes (position, etc.)
  \node (M_block)	[base]	{M};
  \node (E_block)	[base, above of= M_block]	{E};
  \node (W_block)	[base, above of= E_block]	{$W$};
  \node (TE_block)	[tangent, right of= E_block, , xshift=0.4cm]	{$TE$};
  \node (VE_block)	[process, right of= E_block, , xshift=0.4cm]	{$VE$};

  \node (TW_block)	[tangent, right of= W_block, , xshift=0.4cm]	{$TW$};
  \node (VmW_block)	[verticalbig, right of= W_block, , xshift=0.4cm]	{$V_MW$};
  \node (VeW_block)	[verticalsmall, right of= W_block, , xshift=0.4cm]	{$V_EW$};

  \end{tikzpicture}

  \begin{tikzpicture}
    \node[matrix] (A) {
        \draw (0,0) rectangle (1,1); 
        \node at (0.5,0.5) {A}; \\
    };
    \node[matrix,left of=A] (B) 
    {
        \draw (0.5,0.5) circle (0.5);
        \fill (0.5,0.5) circle (0.1); \\
    };
\end{tikzpicture}
\end{document}

### 2017-05-11 ms_landscape.tex
CPS talk notes.

% Geometric Fields Mechanics: Multi-Symplectic approach at glance
% Author: Antonio miti

\documentclass[border=10pt]{standalone}
\usepackage{tikz}
\usepackage[diffgeo]{../Math-Symbols-List/commonmathsymb}

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},
   kinematics/.style = {base, fill=green!20},               
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

\begin{document}

% Drawing part, node distance is 1.5 cm and every node
% is prefilled with white background

\begin{tikzpicture}[node distance=2.25cm,
    every node/.style={fill=white, font=\sffamily}, align=center]

  % Specification of nodes (position, etc.)
  \node (M_block)	[kinematics]	{M};
  \node (volM_block)	[process, left of= M_block, xshift=-0.4cm]	{$\bigwedge^m M$};
  \node (E_block)	[kinematics, above of= M_block]	{E};
  \node (volE_block)	[process, right of= E_block, , xshift=0.4cm]	{$\bigwedge^m E$};
  \node (Z_block)	[process, right of= volE_block]	{$Z$};

  \node (J1E_block)	[lagrangian, above left of= E_block, yshift=1.5cm, xshift=-1cm]	{$J^{1}E$};
  \node (J2E_block)	[lagrangian, above of= J1E_block]	{$J^2E$};
  \node (dualVE_block) [ fill=orange!15,base, left of =E_block, xshift=-2cm] {$V^\TwistedLinear E$};

  \node (affdualJ1E_block)	[hamiltonian, above right of= E_block, yshift=0.5cm, xshift=1cm]	{$J^{1\TwistedAffine}E$};  
  \node (lindualJ1E_block) [hamiltonian, above of =affdualJ1E_block] {$\vec{J}^{1\TwistedLinear}E$};  
  \node (J1lindualJ1E_block) [hamiltonian, above of =lindualJ1E_block] {$J^1 \left( \vec{J}^{1\TwistedLinear} E \right)$}; 
	\node(duallindualJ1E_block)[ fill=cyan!15, base, right of =lindualJ1E_block, xshift=1cm] {$V^\TwistedLinear \left( \vec{J}^{1\TwistedLinear} E \right)$};

  % Bundle Projections 
	\draw[projection]	(E_block) -- (M_block);
	\draw[projection]	(volM_block) -- (M_block);

	\draw[projection]	(volE_block) -- (E_block); 
	\draw[projection]	(J1E_block.south east) -- (E_block); 
	\draw[projection]	(affdualJ1E_block.south west) -- (E_block); 
	\draw[projection]	(lindualJ1E_block.south west) -- (E_block); 
	\draw[projection]	(dualVE_block) -- (E_block);

	\draw[inclusion]	(Z_block) -- (volE_block);
	\draw[projection]	(J2E_block) -- (J1E_block);

	\draw[projection]	([xshift=-0.25cm] affdualJ1E_block.north) -- ([xshift=-0.25cm] lindualJ1E_block.south);
	\draw[projection]	(J1lindualJ1E_block) -- (lindualJ1E_block);
	\draw[projection]	(duallindualJ1E_block) -- (lindualJ1E_block);

  % Dynamics Map
	\draw[lagmap]	(J1E_block) -- node {$\mathcal{L}$}	(volM_block);      
	\draw[lagmap,bend left,->]	(J2E_block.west) -| node[above,anchor= east] {$D_\mathcal{L}$} 	(dualVE_block.north);   
	\draw[lagmap]	(J1E_block.east) -- node {$\mathbb{F}\mathcal{L}$}	(affdualJ1E_block.west);   
	\draw[hammap]	([xshift=+0.25cm] lindualJ1E_block.south) -- node {$\mathcal{H}$}	([xshift=+0.25cm] affdualJ1E_block.north);      
	\draw[bend left,hammap]	(J1lindualJ1E_block.east) -| node[above,anchor= west] {$D_\mathcal{H}$}	(duallindualJ1E_block.north);

	\draw[<->]	(Z_block) -- node {$\Phi$}	(affdualJ1E_block);

  \end{tikzpicture}
\end{document}

### 2017-05-12 cpsviams.tex
Picture Draft!
Sigma map.

@@
 
-\documentclass[12pt]{article}
+\documentclass[a4paper,12pt]{scrartcl}  %Per La Stampa
+\usepackage[a4paper, margin=2cm]{geometry}
 
 \usepackage{amsmath}
-\usepackage[diffgeo]{../Math-Symbols-List/commonmathsymb}
+\usepackage[multisym, geomec,basic]{../Math-Symbols-List/commonmathsymb}
+\usepackage{standalone}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+
+\input{../Latex-Theorem/TheoremTemplateToninus.tex}
+
+	\renewcommand{\AffDualJet}{ J^{1 \TwistedAffine}E }
+	\renewcommand{\LinDualJet}{ \overrightarrow{J^{1 \TwistedLinear}E} }
 
@@
 \begin{figure}
-
+  \centering
+  \includestandalone[mode=buildnew]{ms_landscape}
+  \caption{interesting results}
 \end{figure}
@@
  	\begin{displaymath}
- 	J^1E = \left( \pi_{J^1 M,E} : J^1 M\rightarrow M \right)
+ 	J^1E = \left( \pi_{J^1 M,E} : J^1 E\rightarrow E \right)
  	\end{displaymath} 
@@
  	\begin{displaymath}
- 	J^{1 \TwistedAffine}E = \left( \pi_{J^{1 \TwistedAffine} M,E} : J^{1 \TwistedAffine} M\rightarrow M \right)
+ 	\AffDualJet  = \left( \pi_{ \AffDualJet ,E} : \AffDualJet  \rightarrow E \right)
  	\end{displaymath}
@@
 	\begin{displaymath}
-	\vec{J}^{1 \TwistedLinear}E = \left( \pi_{J^{1 \TwistedLinear} M,E} : J^{1 \TwistedLinear} M\rightarrow M \right)
+		\LinDualJet  = \left( \pi_{ \LinDualJet ,E} : \LinDualJet \rightarrow E \right)
 	\end{displaymath}
@@
 
+\item It turns out that  $\LinDualJet $ carries a naturally defined multisymplectic form $\omega = -\textrm{d} \theta$ derived by a multicanonical m-form $\theta$. \\
+	(This has been obtained pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.) \\
+	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.
+
+\item The dynamics can be implemented in two alternative way, fixing a further structure.\\
+	In the Lagrangian picture is fixed a bundle map:
+	\begin{displaymath}
+		\Lagrangian : J^1 E \rightarrow \bigwedge^m (M)
+	\end{displaymath}
+	while in the Hamiltonian framework si fixed a section:
+	\begin{displaymath}
+		\Hamiltonian : \LinDualJet \rightarrow \AffDualJet
+	\end{displaymath}
+
+\item Both of them determine a \emph{Legendre map} computed as a fiber derivative.
+	Mainly we are interested  in
+	\begin{displaymath}
+		\mathbb{F} \Lagrangian : J^1 E \rightarrow \AffDualJet		
+	\end{displaymath}
+	The two dynamics function can be considered equivalent under the condition of \emph{hyper-regularity}\cite[chapter, p.~215]{Gimmsy}.
+
+\item Via $\mathbb{F} \Lagrangian$ we can pull-back the canonical forms on $J^1 E$ to give the \emph{Poincarè - Cartan forms}
+	\begin{displaymath}
+		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta \qquad \omega_\Lagrangian = - \textrm{d} \theta_\Lagrangian
+	\end{displaymath}
+	and via $\Hamiltonian$ we can pull-back the canonical forms on $\LinDualJet$ to give the \emph{De Donder - Weyl forms}
+	\begin{displaymath}
+		\theta_\Hamiltonian = \Hamiltonian^\ast \theta \qquad \omega_\Hamiltonian = - \textrm{d} \theta_\Lagrangian
+	\end{displaymath}
+
+\item At last, are introduced the \emph{Euler-Lagrange map}
+	\begin{displaymath}
+		D_\Lagrangian : J^2 E \rightarrow V^\TwistedLinear E
+	\end{displaymath}
+	 a bundle-morphism acting on holonomic section submanifolds $\varphi(M)$ as:
+	\begin{displaymath}
+		\left\langle D_\Lagrangian(\varphi, \partial \varphi , \partial^2 \varphi) \right\vert \left. V \right\rangle = (j^1 \varphi)^\ast \left( j^1V \lrcorner \omega_\Lagrangian \right)
+	\end{displaymath}
+	 a bundle-morphism when evaluated on a vertical field $V$ on $E$. \\
+	And the \emph{DeDonder-Weyl map}
+	\begin{displaymath}
+		D_\Hamiltonian : J^1\left(\LinDualJet \right) \rightarrow V^\TwistedLinear \left(\LinDualJet \right)
+	\end{displaymath}
+	acting on holonomic section submanifolds $(\varphi, \pi)(M)$ as:
+	\begin{displaymath}
+		\left\langle D_\Hamiltonian(\varphi, \pi, \partial \varphi , \partial \pi) \right\vert \left. V \right\rangle = (\varphi, \pi)^\ast \left( V \lrcorner \omega_\Hamiltonian \right)
+	\end{displaymath}	
+	when evaluated on a vertical field $V$ on $\LinDualJet$.
+
+\item	
+	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-know motion equations when rapresented in coordinate.
+
 \end{itemize}
+
+\section{Covariant phase space approach}
+The gist of the transition from the \emph{multi-symplectic approach} to the \emph{Covariant Functional Approach} - based on the \emph{Covariant Phase Space} - is basically to perform a change of perspective.\\
+We have to move our attention from the bundles to the cross-sections on the bundles.
+
+The smooth bundle $(F:\rightarrow M)$ to be considered depends on the dynamical framework we are employing:
+
+\begin{center}
+\begin{tabular}{|c|c|c|}
+	\hline
+	 & Lagrangian picture & Hamiltonian picture \\
+	\hline
+	$F$		&	$E$		&	$\LinDualJet$	\\
+	$\downarrow$ & $\downarrow$ & $\downarrow$ \\
+	$M$ & $M$ & $M$ \\
+	    & \emph{configuration bundle} & \emph{multiphase bundle} \\
+	\hline
+\end{tabular}
+\end{center}
+
+In this approach there are two central objects:
+
+	\begin{definition}[Space of kinematics (off-shell) configurations]\label{Def:ConfSpace}
+		Is the, generally non-linear, infinte-dimensional manifold :
+		\begin{displaymath}
+			\Conf \coloneqq \Gamma^\infty(F,M)
+		\end{displaymath}
+	\end{definition}
+
+	\begin{definition}[Space of Dynamics (on-shell) configurations]\label{Def:SolSpace}
+		Is the subset of $\Conf$:
+		\begin{displaymath}
+			\Sol \coloneqq \ker(D_\cdot) \subset \Conf
+		\end{displaymath}
+		containing all the smooth solutions of the motion equations corresponding to the  dynamical operator $D_\cdot$.
+	\end{definition}
+
+The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle.
+They have to be composed with the jet functor $j^1$.
+
+\begin{equation}
+	D_\Lagrangian[\; ] = D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[j^2 \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right)
+\end{equation}
+
+\begin{equation}
+	D_\Hamiltonian[\; ] = D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[j^1 (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
+\end{equation}
+
+The target base is a vector space, more precisely a frechet space \cite[Cap.2]{Ban} and makes sense to ask whetever $D_\cdot [\phi]$ is equal to the 0-section.
+
+\begin{notationfix}
+Noticing the recurring scheme we will make use of the following notation:
+	\begin{displaymath}
+		W = V^\TwistedLinear F \; ; \; V = \Gamma^\infty(W,F) \quad \Rightarrow \quad D[\phi] \in V \quad \forall \phi \in \Conf
+	\end{displaymath}
+\end{notationfix}
+
+The remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
+Natural beside the fact that its very structure, as a set, is expicitly determined by the fixed Lagrangian or Hamiltonian.\\
+Therefore, is the candidate to  be the field-theoretic (Covariant) phase space.
+
+Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as a manifold.
+Hence, we have to specify conveniently the structure of their tangent space in order to make clair the preceeding claim.
+
+The first thing to point out is the following chain of inequalities:
+\begin{equation}
+	\Gamma^\infty_c\left(\phi^*(VF)\right) \; \subseteq \; T_\phi\Sol \; \subset \; T_\phi\Conf \; \subseteq \; \Gamma^\infty\left( \phi^\ast (VF) \right)
+\end{equation}
+
+\begin{wrapfigure}{L}{0.50\textwidth}
+\centering
+\includegraphics[width=0.49\textwidth]{Pictures/variations.png}
+\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
+\end{wrapfigure}
+This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
+Therefore, a parametrized regular curve as to be regarded as a family of diffeomerphisms, the flow generated by a vertical tangent field on $F$.\\
+The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.
+
+According to this interpretation, $T_\phi\Sol$ should consits of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.
+A rigourosly, this can be expressed in the following definition:
+
+	\begin{definition}[Tangent space to the Space of Solutions]\label{Def:TangentSol}
+		\begin{displaymath}
+			T_\phi \Sol \coloneqq \ker(J[\phi]_\cdot) \qquad \phi \in \Sol
+		\end{displaymath}
+	\end{definition}
+In other words, it consists of the solutions of the Jacobi equations.
+
+\section{Jacobi Operator}\label{Sec:JacobiOperator}
+Intuitively, the Jacobi equation are the formal linearizazion of the motion equation around a solution $\phi$.\\
+Precisely this can be encoded in the following operator:
+
+	\begin{definition}[Jacobi operator pertaining to $D_\cdot$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp}
+		\begin{displaymath}
+			J[\phi] \; : \; T_\phi \Conf \rightarrow	\phi^\ast(V^\TwistedLinear F) \quad s.t. \quad \left\langle D[\phi] \right.\left| \delta\phi \right\rangle
+			= \sigma \left( \left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \right)
+		\end{displaymath}
+	\end{definition}
+
+\begin{wrapfigure}{L}{0.41\textwidth}
+\centering
+\includegraphics[width=0.40\textwidth]{Pictures/jacobi.png}
+\caption{\footnotesize \label{fig:jacobi}$J[\phi]$ and $D$ target on the same space.}
+\end{wrapfigure}
+where:
+\begin{itemize}
+	\item $\phi_\lambda$ is an arbitrary variation of $\phi_0 = \phi$ generated by $\delta\phi$.
+	\item exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
+		\begin{displaymath}
+			\left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
+			\quad \Rightarrow \quad
+			\left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
+		\end{displaymath}
+		because $D_\cdot[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$, 
+		thus the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
+		but only from its infinitesimal generator $\delta\phi$.
+	\item $\sigma$ is the canonical bundle-morphism
+		\begin{displaymath}
+			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
+		\end{displaymath}
+		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
+		 and $0$ is the zero-section of $W$ over $F$.
+\end{itemize}
+
+The operator is well defined since
+\begin{displaymath}
+	\phi \in \Sol \quad \Rightarrow \quad D[\phi] \subset 0(E)
+\end{displaymath}
+
+\section{Construction of $\sigma$}
+Consider the two stacked bundle, $ W \rightarrow E$ vector bundle, $E \rightarrow M$ smooth bundle.
+
+where $m$ is the standard bundle morphism of pull-back bundle:
+\begin{displaymath}
+	m : \left( \pi^\ast \left( T E \right) \right)_w = \{w\} \times \{T_{\pi(w)} \} \mapsto T_{\pi(w)} E
+\end{displaymath}
+
+\begin{figure}
+  \centering
+  \includestandalone[mode=buildnew]{ms_sigmaconstruction}
+\end{figure}
+
+We have the following short exact sequence of bundle morphism over $W$
+\begin{figure}
+  \centering
+  \caption{short exact sequence}
+\end{figure}
+because
+
+\begin{displaymath}
+	\ker(i) = 0 (E) = i' \left( 0 \right)
+\end{displaymath}
+\begin{displaymath}
+	\ker\left( T \pi_{E,W} \right) = V_E W = i\left( V_E W \right)
+\end{displaymath}
+\begin{displaymath}
+	\ker\left(T \pi_{M,E}\right) = V_M E = T \pi_{E,W} \left( V_M W \right)
+\end{displaymath}
+
+We can exhibit a right splitting, that is:
+\begin{displaymath}
+	u : C \rightarrow B \quad \textrm{s.t.} \quad u \circ T \pi_{E,W} = \textrm{id}_B
+\end{displaymath}
+so, by splitting lemma, we have a left splitting $\sigma : B \rightarrow A$.
+
+The claimed right splitting is the following:
+\begin{align*}
+		u = T0 \circ m \; : & \; \pi^\ast_{E,W} \left(TE \right) \rightarrow TE \rightarrow TW \\
+						& \{w\} \times \{V_{\pi(w)} \} \mapsto V_{\pi(w)} \mapsto \left( T_{\pi(w)}0\right) (V_{\pi(w)})
+\end{align*}
 
@@
 
-\section{Previous work}\label{previous work}
-A much longer \LaTeXe{} example was written by Gil~\cite{Gil:02}.
+\begin{figure}
+  \centering
+  \includegraphics{Pictures/jacobi.png}
+  \caption{.}
+\end{figure}
 
-\section{Results}\label{results}
-In this section we describe the results.
+\begin{figure}
+  \centering
+  \includegraphics{Pictures/jacobi.png}
+  \caption{.}
+\end{figure}
 
-\section{Conclusions}\label{conclusions}
-We worked hard, and achieved very little.
+\begin{figure}
+  \centering
+  \includegraphics{Pictures/fieldJacobi.png}
+  \caption{.}
+\end{figure}
 
-%\bibliographystyle{abbrv}
-%\bibliography{main}
+\begin{figure}
+  \centering
+  \includegraphics{Pictures/sigma.png}
+  \caption{.}
+\end{figure}
+
+\bibliographystyle{abbrv}
+\bibliography{main}
+\begin{thebibliography}{9}
+
+\bibitem{Gimmsy}
+  Leslie Lamport,
+  \emph{\LaTeX: a document preparation system},
+  Addison Wesley, Massachusetts,
+  2nd edition,
+  1994.
+
+\end{thebibliography}
 

### 2017-05-15 cpsviams.tex
Commutative Diagram

@@
 \usepackage[multisym, geomec,basic]{../Math-Symbols-List/commonmathsymb}
-\usepackage{standalone}
+\usepackage[subpreambles=true]{standalone}
 \usepackage{graphicx}
@@
 \centering
-\includegraphics[width=0.40\textwidth]{Pictures/jacobi.png}
+\includegraphics[width=0.40\textwidth]{Pictures/Jacobi.png}
 \caption{\footnotesize \label{fig:jacobi}$J[\phi]$ and $D$ target on the same space.}
@@
 
-\section{Construction of $\sigma$}
+\subsection{Construction of $\sigma$}
 Consider the two stacked bundle, $ W \rightarrow E$ vector bundle, $E \rightarrow M$ smooth bundle.
@@
   \centering
-  \caption{short exact sequence}
+  \includestandalone[mode=buildnew]{sigma_exact}
 \end{figure}
@@
 \end{align*}
+In fact, since $0 \in \Gamma (W,E)$:
+
+\begin{displaymath}
+	\textrm{T}_e 0 \circ \textrm{T}_\omega \pi_{E,W} V =
+	\textrm{T}_\omega \left( 0 \circ \pi_{E,W} \right) V = 
+	V \qquad \forall V \in \left( V_M W \right)_\omega ,\; \omega \in \pi^-1(e)
+\end{displaymath}
+Therefore, we have the following decomposition:
+
+\begin{displaymath}
+	\left( V_M W \right)_{0(e)} = 
+	i\left[ V_E W \right]_{0(e)} \oplus \left( T_e 0 \left[ V_e E\right] \right)
+\end{displaymath}
+determining an intrinsic mapping 
+\begin{displaymath}
+	\sigma_e : \left( V_M W \right)_{0(e)} \rightarrow \left( V_E W \right)_{0(e)} \simeq W_e
+\end{displaymath}
+
+which is simply a  projection on the first component.
+
+Since we have such projection for all $e \in E$ and it acts fiberwise, it can be regarded as a bundle morphism over $E$:
+\begin{displaymath}
+	\sigma : 0^\ast \left( V_M W \right) \rightarrow 0^\ast \left( V_E W \right) \simeq W
+\end{displaymath}
+
+\begin{wrapfigure}{L}{0.41\textwidth}
+\centering
+\includegraphics[width=0.40\textwidth]{Pictures/sigma.png}
+  %\caption{.}
+\end{wrapfigure}
+Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.41\textwidth]{Pictures/fieldJacobi.png}
+  \caption{.}
+\end{figure}
+
+\newpage
+\section{Covariant approach: pre-symplectic form}
+\begin{wrapfigure}{L}{0.41\textwidth}
+\centering
+\includegraphics[width=0.40\textwidth]{Pictures/symform.png}
+  \caption{(temp)}
+\end{wrapfigure}
+
+Rough strategy:
+\begin{itemize}
+	\item Find a way to contract $\delta \phi$ and $\delta \phi '$ , seen as tangent vector field on $E$, with the multi-symplectic forms $\omega$.
+	\item pull-back the obtained $m-1$ form to $M$, oriented manifold.
+	\item Integrate thus form on a suitable $(m-1)$ dimensional sub-manifold of $M$.
+	\item take the resulting number as the evaluation of the desired form on the two variations.  
+\end{itemize}
+
+Rigourosly, we define $\forall \phi \in \Conf$, $\forall \Sigma \subset M$ $m-1$ dimensional, compact submanifold
+
+\begin{definition}[(covariant) pre-symplectic form in $\phi$ pertaining to $\Sigma$]
+	\begin{displaymath}
+		\Omega_\Gamma ( \phi ) : \textrm{T}_\phi \Conf \times \textrm{T}_\phi \Conf \rightarrow \Real
+\end{displaymath}		
+	S.t:
+	\begin{align*}
+		\left\langle	\Omega_\Sigma ( \varphi) \right.\left\lvert \delta \varphi_1 , \delta \varphi_2 \right\rangle &=		
+		\int_\Gamma (j^1 \varphi)^\ast \left[ i_{\delta\varphi_2} i_{\delta \varphi_1} \omega_\Lagrangian \right]
+		& \qquad \textrm{(Lagrangian framework)} \\
+		\left\langle	\Omega_\Sigma ( \varphi, \pi) \right.\left\lvert ( \delta \varphi_1, \delta \pi_1),
+		( \delta \varphi_2, \delta \pi_2) \right\rangle &=		
+		\int_\Gamma (\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]
+		& \qquad \textrm{(Hamiltonian framework)} 		
+	\end{align*}
+\end{definition}
+
+We can easily recognize that at this level $J^1 E$ and $\LinDualJet$ takes a similar role
 
@@
 Finally, Section~\ref{conclusions} gives the conclusions.
-
-\begin{figure}
-  \centering
-  \includegraphics{Pictures/jacobi.png}
-  \caption{.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{Pictures/jacobi.png}
-  \caption{.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{Pictures/fieldJacobi.png}
-  \caption{.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{Pictures/sigma.png}
-  \caption{.}
-\end{figure}
 

### 2017-05-16 cpsviams.tex
Sigma graph updated

--- 2017-05-12 cpsviams.tex
@@
 
-\section{Introduction: multisymplectic landscape at glance}
+\section{Introduction}
 Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.
@@
   \includestandalone[mode=buildnew]{ms_landscape}
-  \caption{interesting results}
+  \caption{multisymplectic landscape at glance}
 \end{figure}
@@
 \includegraphics[width=0.49\textwidth]{Pictures/variations.png}
-\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
+%\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
 \end{wrapfigure}
+
 This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\

### 2017-05-16 ms_sigmaconstruction.tex
Sigma graph updated

% Geometric Fields Mechanics: Sigma Construction
% Author: Antonio miti

\documentclass[border=10pt]{standalone}
\usepackage{tikz}

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=1cm,
                  text centered, font=\sffamily},
   manifold/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=2.5cm,
                  text centered, font=\sffamily},
   tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},
      tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},               
   verticalsmall/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1cm, minimum height=1cm,
                  text centered, font=\sffamily},
   verticalbig/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1.75cm, minimum height=1.75cm,
                  text centered, font=\sffamily},                              
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

\begin{document}

% Drawing part, node distance is 1.5 cm and every node
% is prefilled with white background

\begin{tikzpicture}[node distance=3.25cm,
    every node/.style={fill=white, font=\sffamily}, align=center]

  % Specification of nodes (position, etc.)
  \node (M_block)	[base]	{M};
  \node (E_block)	[manifold, above of= M_block]	{E};
  \node (W_block)	[manifold, above of= E_block]	{$W$};
  \node (TE_block)	[tangent, right of= E_block, , xshift=0.4cm , label={[label distance=-0.775cm]90:$TE$}]	{};
  \node (VE_block)	[verticalbig, right of= E_block,xshift=0.4cm, yshift=-0.40cm, label={[label distance=-0.7cm]90:$VE$}]	{};

  \node (TW_block)	[tangent, right of= W_block, , xshift=0.4cm , label={[label distance=-0.775cm]90:$TW$}]	{};
  \node (VmW_block)	[verticalbig, right of= W_block, , xshift=0.4cm, yshift=-0.40cm, label={[label distance=-0.7cm]90:$V_M W$}]	{};
  \node (VeW_block)	[verticalsmall, right of= W_block, ,  xshift=0.4cm, yshift=-0.75cm]	{$V_EW$};

  \node (pbTW_block) [ tangent, above right of= TW_block, xshift=0.4cm , label={[label distance=-0.775cm]90:$\pi_{E,W}^\ast\left( TE\right)$}]	{};
  \node (pbVmW_block)	[verticalbig, above right of= TW_block , xshift=0.4cm, yshift=-0.40cm]	{$\pi_{E,W}^\ast\left( TV\right)$};

  \end{tikzpicture}

  \begin{tikzpicture}
    \node[matrix] (A) {
        \draw (0,0) rectangle (1,1); 
        \node at (0.5,0.5) {A}; \\
    };
    \node[matrix,left of=A] (B) 
    {
        \draw (0.5,0.5) circle (0.5);
        \fill (0.5,0.5) circle (0.1); \\
    };
\end{tikzpicture}
\end{document}

### 2017-05-17 cpsviams.tex
Implemented submodules
Almost finished..

@@
 \usepackage{amsmath}
-\usepackage[multisym, geomec,basic]{../Math-Symbols-List/commonmathsymb}
+\usepackage[multisym, geomec,basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
 \usepackage[subpreambles=true]{standalone}
@@
 
-\input{../Latex-Theorem/TheoremTemplateToninus.tex}
+\usepackage{Latex-Theorem/theoremtemplate}
 
@@
 
-The smooth bundle $(F:\rightarrow M)$ to be considered depends on the dynamical framework we are employing:
-
+The smooth bundle to be considered depends on the dynamical framework we are employing.
+We introduce the following notation, in order to treat both formalism at the same time:
+\begin{notation}
 	\begin{center}
@@
 	\end{center}
+\end{notation}
 
@@
 
-The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle.
-They have to be composed with the jet functor $j^1$.
+The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle composing with the jet functor $j$.
 
 \begin{equation}
-	D_\Lagrangian[\; ] = D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[j^2 \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right)
+	D_\Lagrangian[\; ] = D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[ \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right)
 \end{equation}
@@
 \begin{equation}
-	D_\Hamiltonian[\; ] = D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[j^1 (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
+	D_\Hamiltonian[\; ] = D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[ (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
 \end{equation}
@@
 
-\begin{notationfix}
+Again, we would like to employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
+\begin{notation}
+
+	Since operators $D$ when applied to $\phi \in \Conf$ yields a twisted 1-form, 
+	we denote them collectively as $D[\phi] \in \Gamma(\phi^\ast(V^\TwistedLinear F))$.
+	When $D$ is evaluated on a vector field yields
+	\begin{displaymath}
+		\left\langle D[\phi] \right\vert \left. V \right\rangle =
+		\phi^\ast \left( V \lrcorner \omega \right) 
+		\begin{cases}
+			(j^1 \varphi)^\ast \left( j^1V \lrcorner \omega_\Lagrangian \right) \\
+			(\varphi, \pi)^\ast \left( V \lrcorner \omega_\Hamiltonian \right)
+		\end{cases}              
+        \in \Omega^m(M)
+	\end{displaymath}
+
+	where has been employed the following correspondences:
+	\begin{center}
+		\begin{tabular}{|c|c|c|}
+			\hline
+			 & Lagrangian picture & Hamiltonian picture \\
+			\hline
+			$\phi \in \Conf$		&	$j^1 \varphi$		&	$(\varphi, \pi)$	\\
+			$V \in \Gamma(\phi^\ast V F )$ & $j^1 V$ & $V$ \\
+			$\omega$ & $\omega_\Lagrangian$ & $\omega_\Hamiltonian$ \\
+			\hline
+		\end{tabular}
+	\end{center}
+
 	Noticing the recurring scheme we will make use of the following notation:
 	\begin{displaymath}
-		W = V^\TwistedLinear F \; ; \; V = \Gamma^\infty(W,F) \quad \Rightarrow \quad D[\phi] \in V \quad \forall \phi \in \Conf
+		W = V^\TwistedLinear F \; ; \; V = \Gamma^\infty(\phi^\ast W)
 	\end{displaymath}
-\end{notationfix}
+	So,
+	\begin{displaymath}
+		D[\phi] \in V \quad \forall \phi \in \Conf
+	\end{displaymath}
+\end{notation}
 
@@
 
-\begin{wrapfigure}{L}{0.50\textwidth}
+\begin{figure}
 \centering
@@
 %\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
-\end{wrapfigure}
+\end{figure}
 
@@
 The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.
+\begin{notation}
+	\begin{center}
+		\begin{tabular}{|c|c|c|}
+			\hline
+			 & Lagrangian picture & Hamiltonian picture \\
+			\hline
+			$\delta \phi \in T_\phi \Conf$		&	$\delta \varphi$		&	$(\delta \varphi, \delta \pi)$ \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{notation}
 
-According to this interpretation, $T_\phi\Sol$ should consits of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.
-A rigourosly, this can be expressed in the following definition:
+According to this interpretation, $T_\phi\Sol$ should consists of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.
+Rigourosly, this can be expressed in the following definition:
 
@@
 		\begin{displaymath}
-			J[\phi] \; : \; T_\phi \Conf \rightarrow	\phi^\ast(V^\TwistedLinear F) \quad s.t. \quad \left\langle D[\phi] \right.\left| \delta\phi \right\rangle
+			J(\phi) \; : \; T_\phi \Conf \rightarrow	\phi^\ast(V^\TwistedLinear F) 
+			\quad s.t. \quad  \left(J(\phi)\right) [ \delta\phi ]
 			= \sigma \left( \left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \right)
@@
 
-\begin{wrapfigure}{L}{0.41\textwidth}
+\begin{figure}
 \centering
 \includegraphics[width=0.40\textwidth]{Pictures/Jacobi.png}
-\caption{\footnotesize \label{fig:jacobi}$J[\phi]$ and $D$ target on the same space.}
-\end{wrapfigure}
+\caption{\footnotesize \label{fig:jacobi}$ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ target on the same space.}
+\end{figure}
 where:
@@
 \end{displaymath}
+
+\begin{remark}
+	The Jacobi operator $\left(J(\phi) \right) [\delta \phi]$ around a solution $\phi$ when acting on $\delta \phi \in T_\phi \Conf$ yields a twisted form that can be evaluated on a $V \in \Gamma\left(\phi^\ast(V^\TwistedLinear F )\right)$
+\end{remark}
 
@@
 
-\begin{wrapfigure}{L}{0.41\textwidth}
+\begin{figure}
 \centering
@@
   %\caption{.}
-\end{wrapfigure}
+\end{figure}
 Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$
@@
 \section{Covariant approach: pre-symplectic form}
-\begin{wrapfigure}{L}{0.41\textwidth}
+\begin{figure}
 \centering
@@
   \caption{(temp)}
-\end{wrapfigure}
+\end{figure}
 
@@
 
-Rigourosly, we define $\forall \phi \in \Conf$, $\forall \Sigma \subset M$ $m-1$ dimensional, compact submanifold
+Rigourosly, we define $\forall \phi \in \Conf$, $\forall \Sigma \subset M$ $m-1$ dimensional, compact submanifold of $M$:
 
-\begin{definition}[(covariant) pre-symplectic form in $\phi$ pertaining to $\Sigma$]
+\begin{definition}[(covariant) pre-symplectic form in $\phi$ pertaining to $\Sigma$]\label{Def:presymform}
 	\begin{displaymath}
@@
 	S.t:
+	\begin{displaymath}
+		\left\langle	\Omega_\Sigma ( \phi) \right.\left\lvert \delta \phi_1 , \delta \phi_2 \right\rangle =		
+		\int_\Sigma (\phi)^\ast \left[ i_{\delta\phi_2} i_{\delta \phi_1} \omega \right] =
+		\int_\Sigma \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 
+		\begin{cases}
+			\int_\Sigma (j^1 \varphi)^\ast \left[ i_{j^1 \delta\varphi_2} i_{j^1 \delta \varphi_1} \omega_\Lagrangian \right]
+			& \qquad \textrm{(Lagrangian)} \\
+			\int_\Sigma (\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]
+			& \qquad \textrm{(Hamiltonian)} 		
+		\end{cases}
+	\end{displaymath}
+where the form $\Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right)  \in \Omega^{m-1}(M)$ to be integred on $\Sigma$ is called \emph{Symplectic current}.
+\end{definition}
+\begin{notation}
+	The usual notation is still employed:
+	\begin{displaymath}
+		\Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 
+			\begin{cases}
+				(j^1 \varphi)^\ast \left[ i_{j^1 \delta\varphi_2} i_{j^1 \delta \varphi_1} \omega_\Lagrangian \right]
+				& \qquad \textrm{(Lagrangian framework)} \\
+				(\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]
+				& \qquad \textrm{(Hamiltonian framework)} 		
+			\end{cases}	
+	\end{displaymath}
+
+\end{notation}
+
+The form $\Omega_\Sigma (\phi)$ is manifestly bilinear and skew-symmetric but at this stage is far from obvious to prove exactness and non-degeneracy.
+We can not conclude yet that it is a symplectic form.
+However, the clumsy dependence from the choice $\Sigma$ represent a more urgent problem.
+An important remark can be done:
+
+\begin{proposition}\label{Prop:CurrentClosed}
+	When restricted to $\textrm{T}_\phi \Sol$, the symplectic current is a closed form. That is:
+	\begin{displaymath}
+		\textrm{d} \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 0 \qquad \delta \phi_1 , \delta \phi_2 \in T_\phi \Sol
+	\end{displaymath}
+\end{proposition}
+\begin{proof}
+	Working in the collective notation introduced above, we have:
 	\begin{align*}
-		\left\langle	\Omega_\Sigma ( \varphi) \right.\left\lvert \delta \varphi_1 , \delta \varphi_2 \right\rangle &=		
-		\int_\Gamma (j^1 \varphi)^\ast \left[ i_{\delta\varphi_2} i_{\delta \varphi_1} \omega_\Lagrangian \right]
-		& \qquad \textrm{(Lagrangian framework)} \\
-		\left\langle	\Omega_\Sigma ( \varphi, \pi) \right.\left\lvert ( \delta \varphi_1, \delta \pi_1),
-		( \delta \varphi_2, \delta \pi_2) \right\rangle &=		
-		\int_\Gamma (\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]
-		& \qquad \textrm{(Hamiltonian framework)} 		
+		\textrm{d} \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) &= 
+		\phi^\ast \textrm{d} \left[ i_{\delta\phi_2} i_{\delta \phi_1} \omega \right] = 
+		\phi^\ast \left( - i_{\delta\phi_2} \textrm{d} ( i_{\delta \phi_1} \omega )  + \Lie_{\delta\phi_2 } ( i_{\delta \phi_1} \omega ) \right)
 	\end{align*}
-\end{definition}
 
-We can easily recognize that at this level $J^1 E$ and $\LinDualJet$ takes a similar role
+\end{proof}
 
-\paragraph{Outline}
-The remainder of this article is organized as follows.
-Section~\ref{previous work} gives account of previous work.
-Our new and exciting results are described in Section~\ref{results}.
-Finally, Section~\ref{conclusions} gives the conclusions.
+This nice condition represent a sort of exactness condition for the covariant pre-symplectic form.\\
+However, it is not sufficient to eliminate the unwanted dependence from the choice of $\Sigma$.
+In order to get rid of this drawback are to be introduced some other assumptions.\\
+It is customary to require the working condition of physical field system theories on curved background:
+\begin{enumerate}
+	\item $M$ is a \emph{globally-hyperbolic spacetime}
+	\item $\Sigma$ is an arbitrary cauchy surface
+	\item $T_\phi \Conf =\Gamma_{sc} (V^\TwistedLinear F )$ i.e. are only considered space-like compact variations.
+\end{enumerate}
+The first condition guarantees that exists a Cauchy surface and that the spacetime can be folieted according to it $M= \Sigma \times \Real$.\\
+Considering a spacetime \footnote{Oriented, time-oriented, connected, Lorentzian smooth manifold. } allow us to define a space-like compact support.\\
+From last condition follows that for any Cauchy surface $\Sigma$, $ \supp(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \cap \Gamma$ is compact, thus the integration involved in definition \ref{Def:presymform} is always well-defined.
+
+\begin{proposition}
+	In this condition $\Omega_\Sigma (\phi): T_\phi \Sol \times T_\phi \Sol \rightarrow \Real$ does not depends on the choice of $\Sigma$ anymore.
+\end{proposition}
+\begin{proof}
+	Consider 
+	\begin{displaymath}
+		K_t = \supp\left(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \right) \cap \Gamma_t
+	\end{displaymath}
+	by varying $t$, it determines an m-dimensional domain $V \subset M$.
+	For any $U$ open set in $M$ containing $K={K_t}_{0<t<t'}$ we have, as a simple consequence of proposition \ref{Prop:CurrentClosed} and Stokes' lemma, that
+	\begin{displaymath}
+		\int_V \textrm{d} \Upsilon_\phi = - \int_{\Gamma_0} \Upsilon_\phi +\int_{\Gamma_t} \Upsilon_\phi 
+	\end{displaymath}
+	Therefore $\Omega_\Sigma (\phi) = \Omega_{\Sigma'} (\phi)$ for all possible pair of Cauchy surfaces.
+\end{proof}
+
+\begin{wrapfigure}{L}{0.41\textwidth}
+\centering
+\includegraphics[width=0.40\textwidth]{Pictures/sigma.png}
+  %\caption{.}
+\end{wrapfigure}
 

### 2017-05-17 ms_sigmaconstruction.tex
Almost finished..

@@
 
-\begin{tikzpicture}[node distance=3.25cm,
+\begin{tikzpicture}[node distance=4cm,
     every node/.style={fill=white, font=\sffamily}, align=center]
@@
 
-  \node (pbTW_block) [ tangent, above right of= TW_block, xshift=0.4cm , label={[label distance=-0.775cm]90:$\pi_{E,W}^\ast\left( TE\right)$}]	{};
-  \node (pbVmW_block)	[verticalbig, above right of= TW_block , xshift=0.4cm, yshift=-0.40cm]	{$\pi_{E,W}^\ast\left( TV\right)$};
+  \node (pbTW_block) [ tangent, above right of= TW_block, xshift=0.4cm , label={[label distance=-0.9cm]90:$\pi_{E,W}^\ast\left( TE\right)$}]	{};
+  \node (pbVmW_block)	[verticalbig, above right of= TW_block , xshift=0.4cm, yshift=-0.35cm]	{$\pi_{E,W}^\ast\left( TV\right)$};
+
+  % Bundle Projections 
+	\draw[projection]	(E_block) -- (M_block);
+	\draw[projection]	([xshift=-0.5cm]W_block.south) -- node {$\pi$} ([xshift=-0.5cm]E_block.north);
+	\draw[projection]	(TE_block) -- (E_block);
+	\draw[projection]	(TW_block) -- (W_block);
+	\draw[projection]	(pbTW_block.west) -- (W_block.north);
+
+	\draw[lagmap]	(pbTW_block.south) -- node {$m$}	(TE_block.east);   
+	\draw[projection]	([xshift=-0.5cm]TW_block.south) -- node {$T \pi$}	([xshift=-0.5cm]TE_block.north); 
+	\draw[lagmap]	([xshift=+0.5cm] E_block.north) -- node {$0$}	([xshift=+0.5cm] W_block.south);    
+	\draw[lagmap]	([xshift=+0.5cm] TE_block.north) -- node {$T 0$}	([xshift=+0.5cm] TW_block.south);   	
+	\draw[lagmap]	(pbTW_block) -- node {$T \pi$}	(TW_block);
 
   \end{tikzpicture}
-
-  \begin{tikzpicture}
-    \node[matrix] (A) {
-        \draw (0,0) rectangle (1,1); 
-        \node at (0.5,0.5) {A}; \\
-    };
-    \node[matrix,left of=A] (B) 
-    {
-        \draw (0.5,0.5) circle (0.5);
-        \fill (0.5,0.5) circle (0.1); \\
-    };
-\end{tikzpicture}
 \end{document}

### 2017-05-25 cpsviams.tex
Almost finished....

@@
 \usepackage{amsmath}
-\usepackage[multisym, geomec,basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
+\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
 \usepackage[subpreambles=true]{standalone}
+\usepackage{commath}
+
 \usepackage{graphicx}
@@
 \begin{abstract}
-This is the paper's abstract \ldots
+La costruzione del covariant phase space con la cognizione del formalismo simplettico come descritta nell'articolo di forger romero.
+
+Piccola rivisisazione sulla dimostrazione della corrente simplettica (indipendentemente dal formalismo adottato)
+
+Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
+
 \end{abstract}
@@
 
-\item It turns out that  $\LinDualJet $ carries a naturally defined multisymplectic form $\omega = -\textrm{d} \theta$ derived by a multicanonical m-form $\theta$. \\
+\item It turns out that  $\LinDualJet $ carries a naturally defined multisymplectic form $\omega = -\ExtD \theta$ derived by a multicanonical m-form $\theta$. \\
 	(This has been obtained pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.) \\
@@
 	\begin{displaymath}
-		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta \qquad \omega_\Lagrangian = - \textrm{d} \theta_\Lagrangian
+		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta \qquad \omega_\Lagrangian = - \diff \theta_\Lagrangian
 	\end{displaymath}
@@
 	\begin{displaymath}
-		\theta_\Hamiltonian = \Hamiltonian^\ast \theta \qquad \omega_\Hamiltonian = - \textrm{d} \theta_\Lagrangian
+		\theta_\Hamiltonian = \Hamiltonian^\ast \theta \qquad \omega_\Hamiltonian = - \diff \theta_\Lagrangian
 	\end{displaymath}
@@
 			\quad s.t. \quad  \left(J(\phi)\right) [ \delta\phi ]
-			= \sigma \left( \left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \right)
+			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \right)
 		\end{displaymath}
@@
 		\begin{displaymath}
-			\left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
+			\left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
 			\quad \Rightarrow \quad
-			\left.\dfrac{\textrm{d}}{\textrm{d} \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
+			\left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
 		\end{displaymath}
@@
 	\begin{displaymath}
-		\textrm{d} \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 0 \qquad \delta \phi_1 , \delta \phi_2 \in T_\phi \Sol
+		\diff \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 0 \qquad \delta \phi_1 , \delta \phi_2 \in T_\phi \Sol
 	\end{displaymath}
@@
 \begin{proof}
-	Working in the collective notation introduced above, we have:
+	Working in the collective notation introduced above, considering $\phi \in \Sol$ and $V_i \in T_\phi \Sol$  we have:
 	\begin{align*}
-		\textrm{d} \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) &= 
-		\phi^\ast \textrm{d} \left[ i_{\delta\phi_2} i_{\delta \phi_1} \omega \right] = 
-		\phi^\ast \left( - i_{\delta\phi_2} \textrm{d} ( i_{\delta \phi_1} \omega )  + \Lie_{\delta\phi_2 } ( i_{\delta \phi_1} \omega ) \right)
+		\diff \Upsilon_\phi \left( V_1 , V_2 \right) &= 
+		\phi^\ast \diff \left[ i_{V_2} i_{V_1} \omega \right] = 
+		\phi^\ast \left( - i_{V_2} \diff ( i_{V_1} \omega )  + \Lie_{V_2 } ( i_{V_1} \omega ) \right) =	\\
+		&= \phi^\ast \left( 
+			i_{V_2}i_{V_1} \diff \omega - 
+			\Lie_{V_1 } ( i_{V_2} \omega ) +
+			\Lie_{V_2 } ( i_{V_1} \omega ) +
+			i_{[V_1,V_2]} \omega
+		\right)
 	\end{align*}
-
+	using the Cartan's magic formula twice and the commutation rule between Lie derivative and contraction operator $i_\cdot$.\\
+	The first term vanishes because $\omega= \diff \theta$ is exact by construction.\\
+	The second and the third term vanish because
+	\begin{displaymath}
+		\left\langle \left( J(\phi) \right)[V_i] \right\vert \left. V_j \right\rangle = 
+		\phi^\ast \Lie_{V_i} \left( i_{V_j} \omega \right)
+	\end{displaymath}
+	and $V_i$ are solution of the Jacobi equation
 \end{proof}
@@
 	\begin{displaymath}
-		\int_V \textrm{d} \Upsilon_\phi = - \int_{\Gamma_0} \Upsilon_\phi +\int_{\Gamma_t} \Upsilon_\phi 
+		\int_V \diff \Upsilon_\phi = - \int_{\Gamma_0} \Upsilon_\phi +\int_{\Gamma_t} \Upsilon_\phi 
 	\end{displaymath}
@@
 \end{proof}
+
+\subsection{Example: Hamiltonian Picture}
+Let's work out all the calculation for the specific case: Hamiltonian dynamics.\\
+Consider the following trivializing coordinates on the multiphase space:
+\begin{displaymath}
+	\LinDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A)
+\end{displaymath}
+%
+Dynamics is encoded into the Hamiltonian density $H$:
+\begin{displaymath}
+	\mathcal{H}(x^\mu, q^A, p^\mu_A) = 
+	\left(x^\mu, q^A, p^\mu_A, - H( x^\mu, q^A, p^\mu_A) \: \diff^m x \right)
+\end{displaymath}
+%
+The De Donder - Weyl forms are obtained by the tautological form on $\AffDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A, p)$
+\begin{displaymath}
+	\theta = p^\mu_A \diff q^A \wedge \diff^m x_\mu + p \diff^m x
+\end{displaymath}
+via pull-back
+\begin{displaymath}
+	\theta_\Hamiltonian = p^\mu_A \diff q^a \wedge \diff^m x_\mu - H \diff^m x
+\end{displaymath}
+and external derivation
+\begin{displaymath}
+	\omega_\Hamiltonian = -\diff \theta_\Hamiltonian = \diff q^A \wedge \diff p^\mu_A \wedge \diff^m x_\mu + \diff H \wedge \diff^m x 
+\end{displaymath}
+%
+Contracting $\omega_\Hamiltonian$ with a vertical (w.r.t. $M$) tangent field on $\LinDualJet$
+\begin{displaymath}
+	V = V^A \dfrac{\partial}{\partial q^A} +
+			V^\mu_A \dfrac{\partial}{\partial p^\mu_A}
+\end{displaymath}
+and then pulling back with a section $(\varphi,\pi)$ gives:
+\begin{align*}
+	(\varphi , \pi)^\ast (i_V \omega_\Hamiltonian ) = & 
+	\partial_\mu \pi^\mu_A \, V^A(\varphi,\pi) \, \diff^m x 
+	+ \frac{\partial H}{\partial q^A} (\varphi,\pi) \, V^A(\varphi,\pi) \, \diff^m x + \\
+	 & - \partial_\mu \varphi^A \, V^\mu_A(\varphi,\pi) \, \diff^m x +
+	\frac{\partial H}{\partial p^\mu_A} (\varphi,\pi) \, V^\mu_A(\varphi,\pi) \, \diff^m x
+\end{align*}
+where $(\varphi, \pi)$ has to be intended as $\left(x^\mu, \varphi^A(x), \pi^\mu_A(x)\right)$.
+%
+This leads to an explicit formula for the De Donder Weyl map:
+\begin{align*}
+	\eval{\mathcal{D}_\Hamiltonian \left( j^1 (\varphi, \pi) \right) }_{x} = \biggr( & 
+		x^\mu, \varphi^A(x), \pi^\mu_A(x), \\
+		& \left( \frac{\partial H}{\partial q^A} (\varphi,\pi) + \partial_\mu \pi^\mu_A \right)	\diff q^A \otimes \diff^m x 
+			+ \left( \frac{\partial H}{\partial p^\mu_A} (\varphi,\pi) - \partial_\mu \varphi^A \right)	\diff p^\mu_A \otimes \diff^m x
+		\biggr)
+\end{align*}
+%
+Considering then a variation of sections $(\varphi_\lambda, \pi_\lambda)$ and denoting
+\begin{displaymath}
+	\delta \varphi = 
+	\eval{ \dfrac{\partial}{\partial \lambda} \varphi_\lambda }_{ \lambda=0} =
+	\delta \varphi^i \partial_i	\\
+	\; , \qquad
+	\delta \pi = 
+	\eval{ \dfrac{\partial}{\partial \lambda} \pi_\lambda }_{ \lambda=0} =
+	\delta \pi^i \partial_i
+\end{displaymath}
+can be explicitly compute the directional derivative of the map
+\begin{align*}
+	\eval{ \dfrac{\partial}{\partial \lambda} \mathcal{D}_\Hamiltonian \left( j^1 (\varphi, \pi) \right)}_{ \lambda=0} = &
+	\delta \varphi^A \, \dfrac{\partial}{\partial q^A} + 
+	\delta \pi^\mu_A \dfrac{\partial}{\partial p^\mu_A} + \\
+	& + \left( 
+		\frac{\partial^2 H}{\partial q^B \partial q^A} (\varphi, \pi) \delta \varphi^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial q^A} (\varphi, \pi) \delta \pi^\nu_B +
+		\partial_\mu \delta \pi^\mu_A
+	\right)\diff q^A  \otimes \diff^m x + \\
+	& + \left( 
+		\frac{\partial^2 H}{\partial q^B \partial p^\mu_A} (\varphi, \pi) \delta \varphi^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial p^\mu_A}(\varphi, \pi) \delta \pi^\nu_B -
+		\partial_\mu \delta \varphi^A
+	\right)\diff p^\mu_A  \otimes \diff^m x
+\end{align*}
+where the last two terms determine an explicit expression for the Jacobi operator in the case that $(\varphi,\pi)$ is a solution of the motion equations:
+\begin{align*}
+	J_\Hamiltonian\left( (\varphi, \pi)\right) \left[ (\delta\varphi , \delta \pi ) \right] =
+	& \left( 
+		\frac{\partial^2 H}{\partial q^B \partial q^A} (\varphi, \pi) \delta \varphi^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial q^A} (\varphi, \pi) \delta \pi^\nu_B +
+		\partial_\mu \delta \pi^\mu_A
+	\right)\diff q^A  \otimes \diff^m x + \\
+	& + \left( 
+		\frac{\partial^2 H}{\partial q^B \partial p^\mu_A} (\varphi, \pi) \delta \varphi^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial p^\mu_A}(\varphi, \pi) \delta \pi^\nu_B -
+		\partial_\mu \delta \varphi^A
+	\right)\diff p^\mu_A  \otimes \diff^m x
+\end{align*}
+thus a variation $(\delta \varphi, \delta \pi)$ lies in $\Sol$ if
+\begin{align}\label{Eq.:Jacobi}
+	\partial_\mu \delta \pi^\mu_A &=
+	- \frac{\partial^2 H}{\partial q^B \partial q^A} (\varphi, \pi) \delta \varphi^B
+	- \frac{\partial^2 H}{\partial p^\nu_B \partial q^A} (\varphi, \pi) \delta \pi^\nu_B \\
+		\partial_\mu \delta \varphi^A &=
+		\frac{\partial^2 H}{\partial q^B \partial p^\mu_A} (\varphi, \pi) \delta \varphi^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial p^\mu_A}(\varphi, \pi) \delta \pi^\nu_B
+\end{align}
+%
+Finally, considering two variation $(\delta \varphi_i, \delta \pi_i)$ around a solution $(\varphi,\pi)$ we can compute the symplectic current:
+\begin{align*}
+	\Upsilon_{(\varphi,\pi)} \left( (\delta \varphi_1, \delta \pi_1) , (\delta \varphi_2, \delta \pi_2) \right) = &
+	(\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right] = \\
+	= & (\varphi, \pi)^\ast	\left[ (\delta \varphi_1)^A (\delta \pi_2)^\mu_A - (\delta \varphi_2)^A (\delta \pi_1)^\mu_A \right]	\diff^m x_\mu = \\
+	= & \Upsilon_{(\varphi,\pi)}^\mu \diff \sigma_\mu
+\end{align*}
+where $\diff \sigma_\mu $ is the induced volume form on $\Sigma$ from $M$.\\
+Furthermore the external derivative of the form results:
+\begin{align*}
+	\diff \Upsilon_{(\varphi,\pi)} &\left( (\delta \varphi_1, \delta \pi_1) , (\delta \varphi_2, \delta \pi_2) \right)  =
+	\partial_\mu \Upsilon_{(\varphi,\pi)}^\mu \diff^mx = \\
+	& = (\partial_\mu \delta \varphi_1)^A (\delta \pi_2)^\mu_A - (\partial_\mu \delta \varphi_2)^A (\delta \pi_1)^\mu_A + 
+	(\delta \varphi_1)^A (\partial_\mu  \delta \pi_2)^\mu_A - (\delta \varphi_2)^A (\partial_\mu  \delta \pi_1)^\mu_A
+\end{align*}
+In the case that $(\delta \varphi_i, \delta \pi_i) \in T_{(\varphi,\pi)}\Sol$ we can plug equations \ref{Eq.:Jacobi} in the latter expression giving
+\begin{align*}
+	\partial_\mu \Upsilon_{(\varphi,\pi)}^\mu  =&	 
+	\left(
+		\frac{\partial^2 H}{\partial q^B \partial p^\mu_A} (\varphi,\pi) \delta \varphi_1^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial p^\mu_A} (\varphi,\pi) ( \delta \pi_1)^\nu_B +
+	\right) ( \delta \pi_2)^\mu_A +\\
+	&-\left(
+		\frac{\partial^2 H}{\partial q^B \partial q^A} (\varphi,\pi) \delta \varphi_2^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial q^A} (\varphi,\pi) ( \delta \pi_2)^\nu_B +
+	\right) ( \delta \varphi_1)^A +\\
+	&-\left(
+		\frac{\partial^2 H}{\partial q^B \partial p^\mu_A} (\varphi,\pi) \delta \varphi_2^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial p^\mu_A} (\varphi,\pi) ( \delta \pi_2)^\nu_B +
+	\right) ( \delta \pi_1)^\mu_A +\\
+	&+\left(
+		\frac{\partial^2 H}{\partial q^B \partial q^A} (\varphi,\pi) \delta \varphi_1^B +
+		\frac{\partial^2 H}{\partial p^\nu_B \partial q^A} (\varphi,\pi) ( \delta \pi_1)^\nu_B
+	\right) ( \delta \varphi_2)^A \\
+	&=0
+\end{align*}
+thus proving the closedness of the symplectic current.
 

### 2017-05-26 cpsviams.tex
Almost Finished!

@@
 
-\documentclass[a4paper,12pt]{scrartcl}  %Per La Stampa
+\documentclass[a4paper,12pt,fleqn]{scrartcl}  %Per La Stampa
 \usepackage[a4paper, margin=2cm]{geometry}
@@
 \begin{abstract}
+In questo talk viene dettagliata la costruzione del covariant phase space partendo dal formalismo multisimplettico come descritto nell'artticolo di forger romero.
+
 La costruzione del covariant phase space con la cognizione del formalismo simplettico come descritta nell'articolo di forger romero.
@@
 
+\clearpage \newpage
 \section{Covariant phase space approach}
@@
 	\end{definition}
-
+%
+	\begin{remark}
+		Since the jet functor $j^1$ acts injectively on sections, we can equivalently consider any other holonomic jet sections
+		\begin{displaymath}
+			\Conf \simeq j^k \Gamma^\infty(F)
+		\end{displaymath}
+	\end{remark}	
+%
 	\begin{definition}[Space of Dynamics (on-shell) configurations]\label{Def:SolSpace}
@@
 		\end{displaymath}
-		containing all the smooth solutions of the motion equations corresponding to the  dynamical operator $D_\cdot$.
+		containing all the smooth solutions of the motion equations corresponding to the  dynamical operator $D_\Lagrangian$ or $D_\Hamiltonian$ depending on the framework considered.
 	\end{definition}
@@
 \begin{notation}
-
-	Since operators $D$ when applied to $\phi \in \Conf$ yields a twisted 1-form, 
-	we denote them collectively as $D[\phi] \in \Gamma(\phi^\ast(V^\TwistedLinear F))$.
-	When $D$ is evaluated on a vector field yields
+	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on different order jet bundle over $F$, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
+\begin{displaymath}
+	D[\; ] = \; \Gamma^\infty(F) \ni \phi \quad \mapsto \quad D[ \phi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear F \right)\right)
+\end{displaymath}	
+in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
+//
+	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
 	\begin{displaymath}
 		\left\langle D[\phi] \right\vert \left. V \right\rangle =
-		\phi^\ast \left( V \lrcorner \omega \right) 
+		\phi^\ast \left( i_V \omega \right) 
 		\begin{cases}
-			(j^1 \varphi)^\ast \left( j^1V \lrcorner \omega_\Lagrangian \right) \\
-			(\varphi, \pi)^\ast \left( V \lrcorner \omega_\Hamiltonian \right)
+			(j^1 \varphi)^\ast \left( i_{j^1V} \: \omega_\Lagrangian \right) \\
+			(\varphi, \pi)^\ast \left( i_V \: \omega_\Hamiltonian \right)
 		\end{cases}              
@@
 			\hline
-			$\phi \in \Conf$		&	$j^1 \varphi$		&	$(\varphi, \pi)$	\\
+			$\phi \in \Conf$		&	$j^1 \varphi \; , \quad \varphi \in \Gamma^\infty(E)$		&	$(\varphi, \pi)$	\\
 			$V \in \Gamma(\phi^\ast V F )$ & $j^1 V$ & $V$ \\
@@
 
-	Noticing the recurring scheme we will make use of the following notation:
-	\begin{displaymath}
-		W = V^\TwistedLinear F \; ; \; V = \Gamma^\infty(\phi^\ast W)
-	\end{displaymath}
-	So,
-	\begin{displaymath}
-		D[\phi] \in V \quad \forall \phi \in \Conf
-	\end{displaymath}
+	Noticing the recurring scheme we will also denote $
+		W = V^\TwistedLinear F $
 \end{notation}
@@
 
+\clearpage \newpage
 \section{Jacobi Operator}\label{Sec:JacobiOperator}
@@
 
-	\begin{definition}[Jacobi operator pertaining to $D_\cdot$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp}
+	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
 		\begin{displaymath}
-			J(\phi) \; : \; T_\phi \Conf \rightarrow	\phi^\ast(V^\TwistedLinear F) 
-			\quad s.t. \quad  \left(J(\phi)\right) [ \delta\phi ]
-			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \right)
+			J(\phi) \; : \; \phi^\ast(VF) \rightarrow	\phi^\ast(V^\TwistedLinear F) 
+			\quad s.t. \quad  \left(J(\phi)\right) V
+			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda](x) \right\rvert_{\lambda=0} \right)
 		\end{displaymath}
+		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
+		$\sigma$ is the canonical bundle-morphism
+		\begin{displaymath}
+			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
+		\end{displaymath}
+		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
+		 and $0$ is the zero-section of $W$ over $F$.
 	\end{definition}
-
+	As a bundle-map, $J$ can be naturally interpreted functionally as
+	\begin{displaymath}
+		\left(J(\phi)\right) [\: ] : 
+		\Gamma^\infty\left(\phi^\ast(VF)\right) \rightarrow	
+		\Gamma^\infty \left( 
+		\phi^\ast(V^\TwistedLinear F)
+		\right)
+	\end{displaymath}
+%
 \begin{figure}
@@
 \end{figure}
-where:
-\begin{itemize}
-	\item $\phi_\lambda$ is an arbitrary variation of $\phi_0 = \phi$ generated by $\delta\phi$.
-	\item exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
+%
+Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $ that is vertical w.r.t.
+$M$, the derivative involved has to be intended as the tangent velocity vector, thus $\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]$ is the vertical vector field associated to the infinitesimal variation.
+Exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
 		\begin{displaymath}
@@
 		but only from its infinitesimal generator $\delta\phi$.
-	\item $\sigma$ is the canonical bundle-morphism
-		\begin{displaymath}
-			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
-		\end{displaymath}
-		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
-		 and $0$ is the zero-section of $W$ over $F$.
-\end{itemize}
-
+%
 The operator is well defined since
@@
 
-\begin{remark}
-	The Jacobi operator $\left(J(\phi) \right) [\delta \phi]$ around a solution $\phi$ when acting on $\delta \phi \in T_\phi \Conf$ yields a twisted form that can be evaluated on a $V \in \Gamma\left(\phi^\ast(V^\TwistedLinear F )\right)$
-\end{remark}
+\begin{proposition}\label{Prop:JacobieLie}
+	The Jacobi operator $\left(J(\phi) \right) [\delta \phi]$
+	around a solution $\phi$ when acting on an infinitesimal variation $\delta \phi \in T_\phi \Conf$
+	yields a twisted form that can be evaluated on a $V \in \Gamma\left(V F \right)$
+	such that:
+	\begin{displaymath}	
+		\left\langle \left(J(\phi) \right) [\delta \phi] \right\vert
+		\left. V \right\rangle =
+		\phi^\ast \; \Lie_{\delta \phi} \left( i_V \omega \right)
+	\end{displaymath}
+\end{proposition}
+\begin{proof}
+The explicit action of the Jacobi Operator can be reconstructed as follows:
+\begin{displaymath}
+	D[\phi_\cdot](\cdot): (\lambda, x^\mu) \mapsto
+	\left( x^\mu, \phi_\lambda^A (x), \hat{D}[\phi_\lambda]_A(x) \right)
+	\in V^\TwistedLinear F 
+\end{displaymath}
+%
+\begin{align*}
+	\frac{\partial}{\partial \lambda} \eval{D[\phi_\lambda](\cdot)}_{\lambda=0}:
+	x \mapsto
+	\biggr(& x^\mu, \phi_0^A(x), \hat{D}[\phi_0]_A(x),\\
+	&	
+	\eval{\dfrac{\partial \phi^A(x)}{\partial \lambda}}_{\lambda=0}
+	 \dfrac{\partial}{\partial q^A} + 
+	\eval{\dfrac{\partial \hat{D}[\phi_\lambda]_A(x)}{\partial \lambda}}_{\lambda=0}
+	 \dfrac{\partial}{\partial q_A}	  \biggr)
+	 \in V_M(V^\TwistedLinear F)
+\end{align*}
+\begin{align*}
+	\left(J(\phi)\right) [\: ] (\cdot) =
+	\sigma \frac{\partial}{\partial \lambda} \eval{D[\phi_\lambda](\cdot)}_{\lambda=0}:
+	x \mapsto &
+	\left( x^\mu, \phi_0^A(x), 0,
+	\eval{\dfrac{\partial \hat{D}[\phi_\lambda]_A(x)}{\partial \lambda}}_{\lambda=0}
+	 \dfrac{\partial}{\partial q_A}	  \right)
+	 \in V_F(V^\TwistedLinear F) \\
+	 & \qquad \qquad \qquad \vert\wr \\
+	 &
+		\left( x^\mu, \phi_0^A(x),
+			\eval{\dfrac{\partial \hat{D}[\phi_\lambda]_A(x)}{\partial \lambda}}_{\lambda=0} \right)
+	 		\in V^\TwistedLinear F 
+\end{align*}
+	Therefore for all $x\in M$:
+	\begin{align*}
+		\left\langle \left(J(\phi) \right) [\delta \phi] \right\vert
+		\left. V \right\rangle_x &=
+		\left\langle \left(J(\phi) \right) [\delta \phi] (x) \right\vert
+		\left. V_x \right\rangle =
+		\left\langle \left(J(\phi) \right) [\delta \phi] (x)
+		 \right\vert
+		\left. V_x \right\rangle =\\
+		&=
+		\left\langle\left.		
+		\eval{\dfrac{\partial \hat{D}[\phi_\lambda]_A(x)}{\partial \lambda}}_{\lambda=0}
+		\right\vert
+		 V_x \right\rangle =
+		 \eval{
+		 	\dfrac{\partial}{\partial \lambda}
+		\left\langle\left.			 	
+		 	\hat{D}[\phi_\lambda]
+		 			\right\vert
+		 V \right\rangle _x
+		 }_{\lambda=0}
+	\end{align*}
+	from the linearity of the duality evaluation.\\
+	Plugging in the definition of motion operator we obtain 
+	\begin{displaymath}
+				\left\langle \left(J(\phi) \right) [\delta \phi] \right\vert
+		\left. V \right\rangle =
+		 \eval{
+		 	\dfrac{\partial}{\partial \lambda}
+				\left(
+					\phi^\ast_\lambda \left( i_V \omega \right) \right)
+		 }_{\lambda=0}	=
+		 \phi_0^\ast
+		 \eval{
+				\dfrac{\partial}{\partial \lambda}
+				\left(
+			 		\left(\phi_\lambda \cdot \phi_0^{-1}\right)^\ast
+					\left( i_V \omega \right) \right)
+		 }_{\lambda=0}	=
+		 		\phi_0^\ast \; \Lie_{\delta \phi} \left( i_V \omega \right)
+	\end{displaymath}
+	recognizing that $\left(\phi_\lambda \cdot \phi_0^{-1}\right)$ is the flux generated by $\delta \phi$.
+\end{proof}
 
+\clearpage \newpage
 \subsection{Construction of $\sigma$}
@@
 
-We have the following short exact sequence of bundle morphism over $W$
+We have the following short exact sequence of bundle morphism over $W$:
 \begin{figure}
@@
 \end{figure}
-because
-
+since
+%
 \begin{displaymath}
@@
 
-\newpage
+\clearpage \newpage
 \section{Covariant approach: pre-symplectic form}
@@
 	using the Cartan's magic formula twice and the commutation rule between Lie derivative and contraction operator $i_\cdot$.\\
-	The first term vanishes because $\omega= \diff \theta$ is exact by construction.\\
-	The second and the third term vanish because
+	The first term vanishes because $\omega= - \diff \theta$ is exact by construction.\\
+	The second and the third term vanish because, from proposition \ref{Prop:JacobieLie},
 	\begin{displaymath}
@@
 	\end{displaymath}
-	and $V_i$ are solution of the Jacobi equation
+	and $V_i$ are solution of the Jacobi equation.\\
+	The last term vanishes since the lie bracket of two vertical vector field along $\phi$ is equal to the brackets of two vertical field over $F$ constant on each fiber.
 \end{proof}
@@
 
-\begin{wrapfigure}{L}{0.41\textwidth}
-\centering
-\includegraphics[width=0.40\textwidth]{Pictures/sigma.png}
-  %\caption{.}
-\end{wrapfigure}
-
 \bibliographystyle{abbrv}
@@
 \bibitem{Gimmsy}
-  Leslie Lamport,
-  \emph{\LaTeX: a document preparation system},
-  Addison Wesley, Massachusetts,
-  2nd edition,
-  1994.
+	Gotay, M. J., Isenberg, J., Marsden, J. E., Montgomery,	R. (1998). 
+	Momentum Maps and Classical Relativistic
+	Fields. Part I: Covariant Field Theory, (August 2004), 68. 
+	Retrieved from http://arxiv.org/abs/physics/9801019
+
+\bibitem{primer}
+Benini, M., Dappiaggi, C., Hack, T.-P.
+(2013).
+Quantum Field Theory on Curved Backgrounds — a Primer.
+International Journal of Modern Physics A, 28(17), 1330023.
+https://doi.org/10.1142/S0217751X13300238
+
+\bibitem{forgeromero}
+Forger, M.,  Romero, S. V. (2005). Covariant poisson brackets in geometric field theory. Communications in Mathematical Physics, 256(2), 375–410. https://doi.org/10.1007/s00220-005-1287-8
 

### 2017-05-26 cpsviams.tex
Updating illustrations

@@
 \usepackage{graphicx}
-\usepackage{wrapfig}
+\usepackage{hyperref}
 
@@
 \begin{abstract}
-In questo talk viene dettagliata la costruzione del covariant phase space partendo dal formalismo multisimplettico come descritto nell'artticolo di forger romero.
-
-La costruzione del covariant phase space con la cognizione del formalismo simplettico come descritta nell'articolo di forger romero.
-
-Piccola rivisisazione sulla dimostrazione della corrente simplettica (indipendentemente dal formalismo adottato)
-
-Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
+In this talk we detail the construction of the covariant phase space starting from multisymplectic framework of geometric classic field theories following essentially the paper written by forger romero.
+%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
 
@@
 in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
-//
+\\
 	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
@@
 
-	Noticing the recurring scheme we will also denote $
-		W = V^\TwistedLinear F $
+	Noticing the recurring scheme we will also denote $	W = V^\TwistedLinear F $
 \end{notation}
@@
 \centering
-\includegraphics[width=0.40\textwidth]{Pictures/sigma.png}
+  \includestandalone[mode=buildnew]{sigma}
   %\caption{.}
@@
   \centering
-  \includegraphics[width=0.41\textwidth]{Pictures/fieldJacobi.png}
-  \caption{.}
+    \includestandalone[mode=buildnew]{fieldJacobi}
+  %\caption{.}
 \end{figure}

### 2017-05-26 fieldJacobi.tex
Updating illustrations

\documentclass[border=10pt, tikz]{standalone}
\usepackage{tikz}
\usepackage{tikz-3dplot}
        \usetikzlibrary{patterns,hobby}

\tdplotsetmaincoords{110}{50}

\tikzset{%
  % Specifications for style of arrows:
   M/.style={
           -,
           red,},
   F/.style={
           -,
           blue,},
   W/.style={
           -,
           green,},
   O/.style={
           -,
           gray,},
   hidden/.style={
   			dashed,},                            
}

\def \zlevel {1.25}

\begin{document}

\begin{tikzpicture}[scale=2, tdplot_main_coords,thick]

\node (O) at (0,0,0)  {};
\node (A) at (0,3,0)  {};
\node (B) at (3,3,0)  {};
\node (C) at (3,0,0)  {};

\draw[M] (O.center) -- node [below] {$M$} (A.center);

\draw[F] (A.center) --  node [below right] {$F$} (B.center);
\draw[F,hidden] (B.center) --  node [right] {} (C.center); 
\draw[F,hidden] (C.center) --  node [right] {} (O.center);  
\path[fill=blue!5,opacity=.5] (O.center) to (A.center) to (B.center) to (C.center) to (O.center);

\node (O1) at (0,0,\zlevel)  {};
\node (A1) at (0,3,\zlevel)  {};
\node (B1) at (3,3,\zlevel)  {};
\node (C1) at (3,0,\zlevel)  {};

\draw[O] (O1.center) -- node [below] {$0(F)$} (A1.center); 
\draw[O] (A1.center) --  node [right] {} (B1.center);
\draw[O,hidden] (B1.center) --  node [right] {} (C1.center); 
\draw[O,hidden] (C1.center) --  node [right] {} (O1.center);

\node (O2) at (0,0,3)  {};
\node (A2) at (0,3,3)  {};
\node (B2) at (3,3,3)  {};
\node (C2) at (3,0,3)  {};

\draw[W] (O2.center) -- node [below] {} (A2.center); 
\draw[W] (A2.center) --  node [right] {} (B2.center);
\draw[W] (B2.center) --  node [right] {} (C2.center); 
\draw[W] (C2.center) --  node [above] {$W$} (O2.center);

\draw[W] (O.center) -- node [below] {} (O2.center); 
\draw[W] (A.center) -- node [below] {} (A2.center); 
\draw[W] (B.center) -- node [below] {} (B2.center); 
\draw[W,hidden] (C.center) -- node [below] {} (C2.center);

\path[fill=green!5,opacity=.25] (O.center) to (C.center) to (C2.center) to (O2.center) to (O.center);
\path[fill=green!5,opacity=.25] (C.center) to (B.center) to (B2.center) to (C2.center) to (C.center);
\path[fill=green!5,opacity=.25] (O2.center) to (A2.center) to (B2.center) to (C2.center) to (O2.center);
\path[fill=gray!10,opacity=.25] (O1.center) to (A1.center) to (B1.center) to (C1.center) to (O1.center);

%\node[draw=none,shape=circle,fill, inner sep=2pt] (d1) at (0,1,0){};  % circle

\node (P1) at (1.5,3,\zlevel) {};
\node (P2) at (2.5,3,2.75)  {};
\node (P3) at (1.5,3,2.75)  {};
\draw[-latex,orange] (P1.center) -- node [right] {$V$}	 (P2.center);
\draw[-latex,orange!85] (P1.center) -- node [left] {$\sigma(V)$} (P3.center);
\draw[-latex,dashed,line width=0.5pt,dashed] (P2.center) -- node [above] {$\sigma$} (P3.center);

\node[label={270:{$0(e)$}},circle,fill,inner sep=1pt] (0e) at (1.5,3,\zlevel) {};
\node[label={270:{$e$}},circle,fill,inner sep=1pt] (e) at (1.5,3,0)  {};
\node[label={270:{$x$}},circle,fill,inner sep=1pt] (x) at (0,3,0)  {};

\path[fill=green!5,opacity=.25] (B.center) to (A.center) to (A2.center) to (A2.center) to (B.center);
\path[fill=green!5,opacity=.25] (A.center) to (O.center) to (O2.center) to (O2.center) to (A.center);

    \end{tikzpicture}
    \end{document}

    	%Curva di Partenza
    \draw[red,line width=1pt] (1 ,0,\zlevel)
    .. controls (1.5,0.75,\zlevel)  and (2.5,0.5,\zlevel) .. (1.5,1.5,\zlevel)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Na \p){}
  		}
  	.. controls  (0.5,2.5,\zlevel) .. (P1.center)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Ma \p){}
  		}
  		;

  	%Curva Variata
    \draw[gray,line width=0.5pt,dotted] (1 ,0,\zlevel)
    .. controls (1.95,0.75,1.75)  and (2.8,0.5,2.5) .. (2.25,1.5,2.15)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Nb \p){}
  		}
  	.. controls  (1.5,2.5,\zlevel) .. (P2)
		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
      		node[sloped,inner sep=0cm,above,pos=\p/10,
      			anchor=south west]
      			(Mb \p){}
  		}
  		;
   	%Lo Jacobi Field
    \foreach \p in {0,2,...,8} {
      \draw[-latex,gray,line width=0.65pt,dotted] (Na \p.center) -- (Nb \p.center);
      \draw[-latex,gray,line width=0.65pt,dotted] (Ma \p.center) -- (Mb \p.center);    }

### 2017-05-26 sigma.tex
Updating illustrations

--- 2017-05-26 fieldJacobi.tex
@@
 \usepackage{tikz-3dplot}
+\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
 \usetikzlibrary{patterns,hobby}
@@
 \draw[W] (B2.center) --  node [right] {} (C2.center); 
-\draw[W] (C2.center) --  node [above] {$W$} (O2.center);
+\draw[W] (C2.center) --  node [above] {$V^\TwistedLinear F $} (O2.center);
 
 \draw[W] (O.center) -- node [below] {} (O2.center); 
-\draw[W] (A.center) -- node [below] {} (A2.center); 
+%\draw[W] (A.center) -- node [below] {} (A2.center); 
 \draw[W] (B.center) -- node [below] {} (B2.center); 
@@
 
-\node (P1) at (1.5,3,\zlevel) {};
-\node (P2) at (2.5,3,2.75)  {};
-\node (P3) at (1.5,3,2.75)  {};
-\draw[-latex,orange] (P1.center) -- node [right] {$V$}	 (P2.center);
-\draw[-latex,orange!85] (P1.center) -- node [left] {$\sigma(V)$} (P3.center);
-\draw[-latex,dashed,line width=0.5pt,dashed] (P2.center) -- node [above] {$\sigma$} (P3.center);
-
-\node[label={270:{$0(e)$}},circle,fill,inner sep=1pt] (0e) at (1.5,3,\zlevel) {};
-\node[label={270:{$e$}},circle,fill,inner sep=1pt] (e) at (1.5,3,0)  {};
-\node[label={270:{$x$}},circle,fill,inner sep=1pt] (x) at (0,3,0)  {};
-
-\path[fill=green!5,opacity=.25] (B.center) to (A.center) to (A2.center) to (A2.center) to (B.center);
-\path[fill=green!5,opacity=.25] (A.center) to (O.center) to (O2.center) to (O2.center) to (A.center);
-
-    \end{tikzpicture}
-    \end{document}
+\node (P0) at (0.5,0,\zlevel) {};
+\node (P1) at (1.2,3,\zlevel) {};
+\node (P2) at (2.5,3,\zlevel)  {};
 
     	%Curva di Partenza
-    \draw[red,line width=1pt] (1 ,0,\zlevel)
+    \draw[red,line width=1pt] (P0.center)
     .. controls (1.5,0.75,\zlevel)  and (2.5,0.5,\zlevel) .. (1.5,1.5,\zlevel)
@@
   	%Curva Variata
-    \draw[gray,line width=0.5pt,dotted] (1 ,0,\zlevel)
-    .. controls (1.95,0.75,1.75)  and (2.8,0.5,2.5) .. (2.25,1.5,2.15)
+    \draw[purple,line width=0.5pt,dotted] (P0)+(0.25,0,0)
+    .. controls (1.95,0.75,\zlevel)  and (2.8,0.5,\zlevel) .. (2.35,1.5,\zlevel)
 		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
-      		node[sloped,inner sep=0cm,above,pos=\p/10,
-      			anchor=south west]
+      		node[pos=\p/10]
       			(Nb \p){}
   		}
-  	.. controls  (1.5,2.5,\zlevel) .. (P2)
+  	.. controls  (1.5,2.5,\zlevel) .. (P2.center)
 		\foreach \p in {0,2,...,10}{						%punti per ottenere il vettore variazione
-      		node[sloped,inner sep=0cm,above,pos=\p/10,
-      			anchor=south west]
+      		node[pos=\p/10]
       			(Mb \p){}
@@
    	%Lo Jacobi Field
-    \foreach \p in {0,2,...,8} {
-      \draw[-latex,gray,line width=0.65pt,dotted] (Na \p.center) -- (Nb \p.center);
-      \draw[-latex,gray,line width=0.65pt,dotted] (Ma \p.center) -- (Mb \p.center);    }
+    \foreach \p in {0,2,...,10} {
+      \draw[->,orange,line width=0.65pt] (Na \p.center) -- (Nb \p.center);
+      \draw[->,orange,line width=0.65pt] (Ma \p.center) -- (Mb \p.center);    }
+
+      \node (p) at (1.2,3,\zlevel) [below right,red] {$D[\phi]$};
+	  \node (q) at (2.5,3,\zlevel)  [below right,purple] {$D[\phi_\lambda]$};
+	  \node (r) at (Mb 0)  [above,orange] {$\delta D[\phi]$};
+
+\draw[W] (A.center) -- node [below] {} (A2.center); 
+\path[fill=green!5,opacity=.25] (B.center) to (A.center) to (A2.center) to (A2.center) to (B.center);
+\path[fill=green!5,opacity=.25] (A.center) to (O.center) to (O2.center) to (O2.center) to (A.center);
+
+    \end{tikzpicture}
+    \end{document}

### 2017-05-28 Pictures/Figure_ms_sigmaconstruction.tex
First Version

--- 2017-05-17 ms_sigmaconstruction.tex
@@
   \node (pbTW_block) [ tangent, above right of= TW_block, xshift=0.4cm , label={[label distance=-0.9cm]90:$\pi_{E,W}^\ast\left( TE\right)$}]	{};
-  \node (pbVmW_block)	[verticalbig, above right of= TW_block , xshift=0.4cm, yshift=-0.35cm]	{$\pi_{E,W}^\ast\left( TV\right)$};
+  \node (pbVmW_block)	[verticalbig, above right of= TW_block , xshift=0.4cm, yshift=-0.3cm]	{$\pi_{E,W}^\ast\left( TV\right)$};
 
@@
 
+	% Legend
+	\node (legend) [draw,right=of M_block,align=left,xshift=1cm] {
+								$\longrightarrow$  : Bundle projection%\\
+    };  
   \end{tikzpicture}

### 2017-05-28 cpsviams.tex
First Version

@@
 \author{
-        Antonio Michele Miti \\
+	International Ph.D. Program in "Science" \\
+	"Differential geometry and applications to modern physics" \\
 	Department of Mathematics and Physics\\
@@
 }
-\date{\today}
 
@@
 \usepackage{commath}
+
+\usepackage[italian,english]{babel}
+\usepackage[utf8]{inputenc}
 
@@
 \begin{abstract}
-In this talk we detail the construction of the covariant phase space starting from multisymplectic framework of geometric classic field theories following essentially the paper written by forger romero.
+In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
+In particular we focus our attention on the construction of the \emph{Covariant Phase Space} starting from the multi-symplectic approach to geometric classic field theories.
 %Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
@@
 
-\section{Introduction}
+\section{Multisymplectic landscape at glance}
 Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.
 
-\begin{figure}
-  \centering
-  \includestandalone[mode=buildnew]{ms_landscape}
-  \caption{multisymplectic landscape at glance}
-\end{figure}
+\begin{center}
+  \includestandalone[mode=buildnew]{Pictures/Figure_ms_landscape}
+\end{center}
 
@@
  	that is an affine bundle over $E$.
- \item Then, we considered other two vector bundle derived from the first jet:
+ \item then, we considered other two vector bundle derived from the first jet bundle. 
+ 	The twisted affine dual of $J^1E$ 
  	\begin{displaymath}
@@
  	\end{displaymath}
-	twisted affine dual of $J^1E$ called \emph{"extended multiphase space"}.
+ 	called \emph{"extended multiphase space"} and th twisted linear dual of $J^1 E$
 	\begin{displaymath}
@@
 	\end{displaymath}
-	twisted linear dual of $J^1 E$ called \emph{"standard multiphase space"}. \footnote{It can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}
+	called \emph{"standard multiphase space"} \footnote{$\LinDualJet$ can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}.\\
 	The first one can be also seen as an affine line bundle over the second one.
 
-\item It turns out that  $\LinDualJet $ carries a naturally defined multisymplectic form $\omega = -\ExtD \theta$ derived by a multicanonical m-form $\theta$. \\
-	(This has been obtained pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.) \\
+\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived by a multicanonical m-form $\theta$, obtained by pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
 	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.
 
-\item The dynamics can be implemented in two alternative way, fixing a further structure.\\
-	In the Lagrangian picture is fixed a bundle map:
+\item Dynamics can be implemented in two different way by fixing a further structure.\\
+	In the Lagrangian picture has to be fixed a bundle map:
 	\begin{displaymath}
@@
 	\end{displaymath}
-	while in the Hamiltonian framework si fixed a section:
+	, called \emph{Lagrangian density}, 	while in the Hamiltonian framework has to be fixed a section:
 	\begin{displaymath}
@@
 	\end{displaymath}
+	called \emph{Hamiltonian density}.
 
-\item Both of them determine a \emph{Legendre map} computed as a fiber derivative.
-	Mainly we are interested  in
+\item Both of them determine a \emph{Legendre map}, computed as a fiber derivative, which allows us to move from one framework to another.
+	Mainly we are interested  in the following:
 	\begin{displaymath}
@@
 	\end{displaymath}
-	The two dynamics function can be considered equivalent under the condition of \emph{hyper-regularity}\cite[chapter, p.~215]{Gimmsy}.
+	The two dynamics function $\Lagrangian$ and $\Hamiltonian$ can be considered equivalent under the condition of \emph{hyper-regularity}\cite[chapter, p.~215]{Gimmsy}.
 
-\item Via $\mathbb{F} \Lagrangian$ we can pull-back the canonical forms on $J^1 E$ to give the \emph{Poincarè - Cartan forms}
+\item Via $\mathbb{F} \Lagrangian$ we can pull-back the canonical forms on $J^1 E$ to give the \emph{Poincaré - Cartan forms} giving:
 	\begin{displaymath}
-		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta \qquad \omega_\Lagrangian = - \diff \theta_\Lagrangian
+		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta 
+		\qquad 
+		\omega_\Lagrangian = - \diff \theta_\Lagrangian
 	\end{displaymath}
-	and via $\Hamiltonian$ we can pull-back the canonical forms on $\LinDualJet$ to give the \emph{De Donder - Weyl forms}
+	Via $\Hamiltonian$ we can pull-back the canonical forms on $\LinDualJet$ to give the \emph{De Donder - Weyl forms} giving:
 	\begin{displaymath}
-		\theta_\Hamiltonian = \Hamiltonian^\ast \theta \qquad \omega_\Hamiltonian = - \diff \theta_\Lagrangian
+		\theta_\Hamiltonian = \Hamiltonian^\ast \theta 
+		\qquad 
+		\omega_\Hamiltonian = - \diff \theta_\Lagrangian
 	\end{displaymath}
 
-\item At last, are introduced the \emph{Euler-Lagrange map}
+\item At last, can be introduced two map in order to encoded the field equations.
+	In the Lagrangian framework we consider the \emph{Euler-Lagrange map}
 	\begin{displaymath}
@@
 	\end{displaymath}
-	 a bundle-morphism when evaluated on a vertical field $V$ on $E$. \\
-	And the \emph{DeDonder-Weyl map}
+	 a bundle-morphism when evaluated on a vertical field $V$ on $E$.\\
+	In the Hamiltonian framework we consider the \emph{DeDonder-Weyl map}
 	\begin{displaymath}
@@
 \item	
-	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-know motion equations when rapresented in coordinate.
+	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-know motion equations when represented in local coordinate charts.
 
@@
 \section{Covariant phase space approach}
-The gist of the transition from the \emph{multi-symplectic approach} to the \emph{Covariant Functional Approach} - based on the \emph{Covariant Phase Space} - is basically to perform a change of perspective.\\
+The gist of the transition from the \emph{multi-symplectic approach} to the \emph{(Covariant) Functional Approach} - based on the \emph{Covariant Phase Space} - is basically to perform a change of perspective.\\
 We have to move our attention from the bundles to the cross-sections on the bundles.
@@
 	\begin{remark}
-		Since the jet functor $j^1$ acts injectively on sections, we can equivalently consider any other holonomic jet sections
+		The jet functor $j^1$ acts injectively on smooth cross sections
 		\begin{displaymath}
@@
 		\end{displaymath}
+		so, we can equivalently consider holonomic jet sections of any order as the element of the configuration space.
 	\end{remark}	
@@
 The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle composing with the jet functor $j$.
-
-\begin{equation}
-	D_\Lagrangian[\; ] = D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[ \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right)
-\end{equation}
-
-\begin{equation}
-	D_\Hamiltonian[\; ] = D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[ (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
-\end{equation}
-
+%
+\begin{align*}
+	D_\Lagrangian[\; ] &= 
+	D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[ \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right) \\
+	D_\Hamiltonian[\; ] &= 
+	D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[ (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
+\end{align*}
+%
 The target base is a vector space, more precisely a frechet space \cite[Cap.2]{Ban} and makes sense to ask whetever $D_\cdot [\phi]$ is equal to the 0-section.
@@
 \begin{notation}
-	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on different order jet bundle over $F$, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
+	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend jet bundle over $F$ of different order, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
 \begin{displaymath}
@@
 	\end{center}	
-
-	Noticing the recurring scheme we will also denote $	W = V^\TwistedLinear F $
+	%
+	Noticing the recurring scheme we will also denote $	W = V^\TwistedLinear F $.
 \end{notation}
 
-The remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
+Remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
 Natural beside the fact that its very structure, as a set, is expicitly determined by the fixed Lagrangian or Hamiltonian.\\
@@
 
+\begin{center}
+\includegraphics[width=0.49\textwidth]{Pictures/variations.png}
+%\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
+\end{center}
+
 Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as a manifold.
-Hence, we have to specify conveniently the structure of their tangent space in order to make clair the preceeding claim.
+Hence, we have to specify conveniently the structure of their tangent space in order to make clear the previous claim.
 
 The first thing to point out is the following chain of inequalities:
-\begin{equation}
+\begin{displaymath}
 	\Gamma^\infty_c\left(\phi^*(VF)\right) \; \subseteq \; T_\phi\Sol \; \subset \; T_\phi\Conf \; \subseteq \; \Gamma^\infty\left( \phi^\ast (VF) \right)
-\end{equation}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{Pictures/variations.png}
-%\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
-\end{figure}
-
+\end{displaymath}
+%
 This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
@@
 
-According to this interpretation, $T_\phi\Sol$ should consists of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.
+According to this interpretation, $T_\phi\Sol$ should consists of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.\\
+In other words, it consists of the solutions of the \emph{Jacobi equations}.
 Rigourosly, this can be expressed in the following definition:
+	\begin{definition}[Tangent space to the Space of Solutions]\label{Def:TangentSol}
+		on a solution $\phi \in \Sol$, is the vector space
+		\begin{displaymath}
+			T_\phi \Sol \coloneqq \ker(J[\phi]_\cdot)
+		\end{displaymath}
+		where $J$ is the so-called \emph{Jacobi Operator}.
+	\end{definition}
 
-	\begin{definition}[Tangent space to the Space of Solutions]\label{Def:TangentSol}
-		\begin{displaymath}
-			T_\phi \Sol \coloneqq \ker(J[\phi]_\cdot) \qquad \phi \in \Sol
-		\end{displaymath}
-	\end{definition}
-In other words, it consists of the solutions of the Jacobi equations.
-
-\clearpage \newpage
 \section{Jacobi Operator}\label{Sec:JacobiOperator}
-Intuitively, the Jacobi equation are the formal linearizazion of the motion equation around a solution $\phi$.\\
-Precisely this can be encoded in the following operator:
-
+Intuitively, the Jacobi equation are the formal linearization of the motion equation around a solution $\phi$.\\
+Precisely they can be encoded in the following operator:
+%
 	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
@@
 		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
-		$\sigma$ is the canonical bundle-morphism
+		$\sigma$ is the canonical bundle-morphism \footnote{see \ref{Section:sigma} for further details.}
 		\begin{displaymath}
@@
 	\end{definition}
-	As a bundle-map, $J$ can be naturally interpreted functionally as
+	%
+	\begin{remark}
+		Being $J$ a bundle morphism, it can be naturally interpreted functionally as
 		\begin{displaymath}
@@
 		\end{displaymath}
+	\end{remark}
 %
-\begin{figure}
-\centering
-\includegraphics[width=0.40\textwidth]{Pictures/Jacobi.png}
-\caption{\footnotesize \label{fig:jacobi}$ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ target on the same space.}
-\end{figure}
-%
-Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $ that is vertical w.r.t.
-$M$, the derivative involved has to be intended as the tangent velocity vector, thus $\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]$ is the vertical vector field associated to the infinitesimal variation.
+  \begin{minipage}[r]{0.5\textwidth}
+    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
+  \end{minipage}\hfill
+  \begin{minipage}[l]{0.5\textwidth}
+	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ target on the same space.
+  \end{minipage}
+
+Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $, that is also vertical w.r.t. $M$, 
+the derivative involved has to be intended as the tangent velocity vector,
+thus $\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]$ is the vertical vector field associated to the infinitesimal variation.\\
 Exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
 		\begin{displaymath}
-			\left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
+			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
 			\quad \Rightarrow \quad
-			\left.\dfrac{\diff}{\diff \lambda} D_\cdot [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
+			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
 		\end{displaymath}
-		because $D_\cdot[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$, 
-		thus the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
+		because $D[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$.
+		Hence the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
 		but only from its infinitesimal generator $\delta\phi$.
-%
-The operator is well defined since
+
+Furthermore, since
 \begin{displaymath}
@@
 \end{displaymath}
+the action of $\sigma$ is legit and operator $J$ results well-defined.
+%
 
-\begin{proposition}\label{Prop:JacobieLie}
+\begin{lemma}\label{Prop:JacobieLie}
 	The Jacobi operator $\left(J(\phi) \right) [\delta \phi]$
 	around a solution $\phi$ when acting on an infinitesimal variation $\delta \phi \in T_\phi \Conf$
-	yields a twisted form that can be evaluated on a $V \in \Gamma\left(V F \right)$
-	such that:
+	yields a twisted form that can be evaluated on any $V \in \Gamma\left(V F \right)$
+	yields the following expression:
 	\begin{displaymath}	
@@
 	\end{displaymath}
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 	&	
-	\eval{\dfrac{\partial \phi^A(x)}{\partial \lambda}}_{\lambda=0}
+	\eval{\dfrac{\partial \phi^A_\lambda(x)}{\partial \lambda}}_{\lambda=0}
 	 \dfrac{\partial}{\partial q^A} + 
@@
 	\end{align*}
-	from the linearity of the duality evaluation.\\
-	Plugging in the definition of motion operator we obtain 
+	from the linearity of the twisted duality pairing $<\,|\,>$.\\
+	Plugging  the definition of motion operator $D$ in the latter expression, we obtain:
 	\begin{displaymath}
@@
 
-\clearpage \newpage
-\subsection{Construction of $\sigma$}
+\newpage
+\subsection{Construction of $\sigma$}\label{Section:sigma}
 Consider the two stacked bundle, $ W \rightarrow E$ vector bundle, $E \rightarrow M$ smooth bundle.
-
-where $m$ is the standard bundle morphism of pull-back bundle:
+	\begin{center}
+	  \includestandalone[mode=buildnew]{Pictures/Figure_ms_sigmaconstruction}
+	\end{center}
+%
+Let us call $m$ the standard bundle morphism of pull-back bundles:
 \begin{displaymath}
@@
 
-\begin{figure}
-  \centering
-  \includestandalone[mode=buildnew]{ms_sigmaconstruction}
-\end{figure}
-
 We have the following short exact sequence of bundle morphism over $W$:
-\begin{figure}
-  \centering
-  \includestandalone[mode=buildnew]{sigma_exact}
-\end{figure}
-since
+	\begin{center}
+	  \includestandalone[mode=buildnew]{Pictures/Figure_sigma_exact}
+	\end{center}
+inasmuch as
 %
-\begin{displaymath}
+\begin{eqnarray*}
 	\ker(i) = 0 (E) = i' \left( 0 \right)
-\end{displaymath}
-\begin{displaymath}
 	\ker\left( T \pi_{E,W} \right) = V_E W = i\left( V_E W \right)
-\end{displaymath}
-\begin{displaymath}
 	\ker\left(T \pi_{M,E}\right) = V_M E = T \pi_{E,W} \left( V_M W \right)
-\end{displaymath}
+\end{eqnarray*}
 
@@
 \end{displaymath}
-so, by splitting lemma, we have a left splitting $\sigma : B \rightarrow A$.
+so, by splitting lemma, we have a left splitting $\sigma : B \rightarrow A$ that is exactly the searched operator.
 
 The claimed right splitting is the following:
-\begin{align*}
-		u = T0 \circ m \; : & \; \pi^\ast_{E,W} \left(TE \right) \rightarrow TE \rightarrow TW \\
-						& \{w\} \times \{V_{\pi(w)} \} \mapsto V_{\pi(w)} \mapsto \left( T_{\pi(w)}0\right) (V_{\pi(w)})
-\end{align*}
-In fact, since $0 \in \Gamma (W,E)$:
-
+	\begin{displaymath}
+		u = T0 \circ m \; : \; 
+		\begin{array}{ccc}
+			\pi^\ast_{E,W} \left(TE \right) &\rightarrow TE &\rightarrow TW \\
+			\{w\} \times \{V_{\pi(w)} \} &\mapsto V_{\pi(w)} &\mapsto \left( T_{\pi(w)}0\right) (V_{\pi(w)})		
+		\end{array}
+	\end{displaymath}
+%
+In fact, since $0 \in \Gamma (W,E)$, we have:
 \begin{displaymath}
@@
 \end{displaymath}
-determining an intrinsic mapping 
+which determine an intrinsic mapping 
 \begin{displaymath}
@@
 \end{displaymath}
-
-which is simply a  projection on the first component.
+that is simply the projection on the first component.
 
@@
 \end{displaymath} 
+Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$.
+%
 
-\begin{figure}
+\begin{minipage}{.5\textwidth}
   \centering
-  \includestandalone[mode=buildnew]{sigma}
-  %\caption{.}
-\end{figure}
-Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$
+	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaAction}
+ \\ \small{general case}
+\end{minipage}
+\begin{minipage}{.5\textwidth}
+  \centering
+	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaJacobi}
+ \\ \small{ (Jacobi field variation)}
+\end{minipage}%
 
-\begin{figure}
-  \centering
-    \includestandalone[mode=buildnew]{fieldJacobi}
-  %\caption{.}
-\end{figure}
+\newpage
+\section{Covariant approach: pre-symplectic form}
+ Roughly, the strategy of construction is the following:
+	\vspace{0.5cm}
 
-\clearpage \newpage
-\section{Covariant approach: pre-symplectic form}
-\begin{figure}
-\centering
-\includegraphics[width=0.40\textwidth]{Pictures/symform.png}
-  \caption{(temp)}
-\end{figure}
-
-Rough strategy:
+  \begin{minipage}[l]{0.5\textwidth}
+	\includegraphics[width=\textwidth]{Pictures/symform.png}
+  \end{minipage}\hfill
+  \begin{minipage}[r]{0.45\textwidth}
 	\begin{itemize}
@@
 	\end{itemize}
+  \end{minipage}\hfill
 
-Rigourosly, we define $\forall \phi \in \Conf$, $\forall \Sigma \subset M$ $m-1$ dimensional, compact submanifold of $M$:
+  	\vspace{1cm}
 
+Rigourosly, fixed  $\Sigma$, a compact $m-1$ dimensional submanifold of $M$, we define:
 \begin{definition}[(covariant) pre-symplectic form in $\phi$ pertaining to $\Sigma$]\label{Def:presymform}
@@
 			\int_\Sigma (j^1 \varphi)^\ast \left[ i_{j^1 \delta\varphi_2} i_{j^1 \delta \varphi_1} \omega_\Lagrangian \right]
-			& \qquad \textrm{(Lagrangian)} \\
+			\\
 			\int_\Sigma (\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]	
-			& \qquad \textrm{(Hamiltonian)} 		
 		\end{cases}
@@
 
-The form $\Omega_\Sigma (\phi)$ is manifestly bilinear and skew-symmetric but at this stage is far from obvious to prove exactness and non-degeneracy.
+The form $\Omega_\Sigma (\phi)$ is manifestly bilinear and skew-symmetric but it is far from obvious, at this stage, to prove exactness and non-degeneracy.
 We can not conclude yet that it is a symplectic form.
@@
 \begin{proposition}\label{Prop:CurrentClosed}
-	When restricted to $\textrm{T}_\phi \Sol$, the symplectic current is a closed form. That is:
+	When restricted to $\textrm{T}_\phi \Sol$, the symplectic current is a closed form:
 	\begin{displaymath}
@@
 However, it is not sufficient to eliminate the unwanted dependence from the choice of $\Sigma$.
-In order to get rid of this drawback are to be introduced some other assumptions.\\
-It is customary to require the working condition of physical field system theories on curved background:
+In order to get rid of this drawback is necessary to introduce some other assumptions.\\
+It is customary to require the working condition of physical field system theories on curved background\cite{primer}:
 \begin{enumerate}
@@
 \end{enumerate}
-The first condition guarantees that exists a Cauchy surface and that the spacetime can be folieted according to it $M= \Sigma \times \Real$.\\
+%
 Considering a spacetime \footnote{Oriented, time-oriented, connected, Lorentzian smooth manifold. } allow us to define a space-like compact support.\\
-From last condition follows that for any Cauchy surface $\Sigma$, $ \supp(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \cap \Gamma$ is compact, thus the integration involved in definition \ref{Def:presymform} is always well-defined.
+So, the first condition guarantees that exists a Cauchy surface and that the spacetime can be foliated according to it $M= \Sigma \times \Real$.\\
+Whereas, from the last condition, follows that for any Cauchy surface $\Sigma$, $ \supp(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \cap \Gamma$ is compact, thus the integration involved in definition \ref{Def:presymform} is always well-defined.
 
@@
 \subsection{Example: Hamiltonian Picture}
-Let's work out all the calculation for the specific case: Hamiltonian dynamics.\\
-Consider the following trivializing coordinates on the multiphase space:
+Let us work out all the calculation for the specific case: Hamiltonian dynamics.\\
+Consider the following trivializing coordinates chart on the multiphase space:
 \begin{displaymath}
@@
 %
-The De Donder - Weyl forms are obtained by the tautological form on $\AffDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A, p)$
+De Donder-Weyl forms are obtained from the tautological form on $\AffDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A, p)$
 \begin{displaymath}
@@
 \end{displaymath}
-can be explicitly compute the directional derivative of the map
+can be explicitly computed the directional derivative of the map
 \begin{align*}
-	\eval{ \dfrac{\partial}{\partial \lambda} \mathcal{D}_\Hamiltonian \left( j^1 (\varphi, \pi) \right)}_{ \lambda=0} = &
+	\hat{\left[\eval{ \dfrac{\partial}{\partial \lambda} \mathcal{D}_\Hamiltonian \left( j^1 (\varphi, \pi) \right)}_{ \lambda=0} \right]}
+	= &
 	\delta \varphi^A \, \dfrac{\partial}{\partial q^A} + 
@@
 
+\bibitem{forgeromero}
+Forger, M.,  Romero, S. V. (2005). Covariant Poisson brackets in geometric field theory. 
+Communications in Mathematical Physics, 256(2), 375–410. 
+https://doi.org/10.1007/s00220-005-1287-8
+
 \bibitem{Gimmsy}
@@
 \bibitem{primer}
-Benini, M., Dappiaggi, C., Hack, T.-P.
-(2013).
-Quantum Field Theory on Curved Backgrounds — a Primer.
+Benini, M., Dappiaggi, C., Hack, T.-P. (2013). Quantum Field Theory on Curved Backgrounds — a Primer. 
 International Journal of Modern Physics A, 28(17), 1330023. 
@@
 
-\bibitem{forgeromero}
-Forger, M.,  Romero, S. V. (2005). Covariant poisson brackets in geometric field theory. Communications in Mathematical Physics, 256(2), 375–410. https://doi.org/10.1007/s00220-005-1287-8
+\bibitem{Ban}
+Ban, E., Crainic, M. (2009). Analysis on Manifolds.
+https://www.staff.science.uu.nl/~ban00101/anman2009/anman2009.html
 

### 2017-05-31 Pictures/Figure_ms_landscape.tex
First Version
Implemented corrections by MS.

--- 2017-05-11 ms_landscape.tex
@@
 
-\documentclass[border=10pt]{standalone}
+\documentclass[border=10pt, tikz]{standalone}
 \usepackage{tikz}
-\usepackage[diffgeo]{../Math-Symbols-List/commonmathsymb}
+\usepackage[multisym, geomec, basic, diffgeo]{../Math-Symbols-List/toninus-math-symbols}
 
@@
    lagmap/.style={
-           projection,
+           -latex,
            red},
    hammap/.style={
-           projection,
+           -latex,
            blue},
@@
 
-	\draw[inclusion]	(Z_block) -- (volE_block);
+	\draw[inclusion]	(Z_block) -- node[above]{$i$} (volE_block);
 	\draw[projection]	(J2E_block) -- (J1E_block);
@@
 	\draw[lagmap]	(J1E_block) -- node {$\mathcal{L}$}	(volM_block);      
-	\draw[lagmap,bend left,->]	(J2E_block.west) -| node[above,anchor= east] {$D_\mathcal{L}$} 	(dualVE_block.north);   
+	\draw[lagmap,bend left]	(J2E_block.west) -| node[above,anchor= east] {$D_\mathcal{L}$} 	(dualVE_block.north);   
 	\draw[lagmap]	(J1E_block.east) -- node {$\mathbb{F}\mathcal{L}$}	(affdualJ1E_block.west);   
@@
 
+	% Legend
+	\node (legend) [draw,right=of M_block,align=left] {
+								$\longrightarrow$ \; : Bundle projection%\\
+    };
+
   \end{tikzpicture}

### 2017-05-31 Pictures/Figure_ms_sigmaconstruction.tex
Implemented corrections by MS.

@@
 
-\usetikzlibrary{arrows,positioning}
+\usetikzlibrary{arrows.meta,positioning}
 \tikzset{%
@@
    projection/.style={
-           ->,
+           -Stealth,
            shorten <=1pt,
@@
   % Specification of nodes (position, etc.)
-  \node (M_block)	[base]	{M};
+  \node (M_block)	[base,yshift=5cm]	{M};
   \node (E_block)	[manifold, above of= M_block]	{E};
@@
 	% Legend
-	\node (legend) [draw,right=of M_block,align=left,xshift=1cm] {
+	\node (legend) [draw,right=of M_block,align=left,xshift=3cm] {
 								$\longrightarrow$  : Bundle projection%\\

### 2017-05-31 cpsviams.tex
Implemented corrections by MS.

@@
 	Department of Mathematics and Physics\\
-	Università Cattolica del Sacro Cuore\\
-	via Musei X, Brescia xxx, \underline{Italy}
+	Universit\'a Cattolica del Sacro Cuore\\
+	via Musei 41, 25121 Brescia, \underline{Italy}
 }
@@
 In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
-In particular we focus our attention on the construction of the \emph{Covariant Phase Space} starting from the multi-symplectic approach to geometric classic field theories.
+In particular we focus our attention on the construction of the \emph{Covariant Phase Space}, starting from the multi-symplectic approach to geometric classic field theories.
 %Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
@@
 
-\section{Multisymplectic landscape at glance}
-Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.
+\section{A glance at the Multisymplectic landscape}
+Let us briefly recall the basics of the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.
 
 \begin{center}
-  \includestandalone[mode=buildnew]{Pictures/Figure_ms_landscape}
+  \includestandalone{Pictures/Figure_ms_landscape}
 \end{center}
@@
 \begin{itemize}
- \item the starting point is the \emph{configuration bundle} 
+ \item The starting point is the \emph{configuration bundle} 
  	\begin{displaymath}
@@
  	the object encoding the kinematics.
- \item from that we have constructed the \emph{I jet bundle} applying the jet functor to $E$ 
+ \item From that we have constructed the \emph{first jet bundle}, applying the jet functor to $E$ 
  	\begin{displaymath}
@@
  	\end{displaymath} 
- 	that is an affine bundle over $E$.
- \item then, we considered other two vector bundle derived from the first jet bundle. 
- 	The twisted affine dual of $J^1E$ 
+ 	which is an affine bundle over $E$.
+ \item Then, we considered two other vector bundles derived from the first jet bundle: 
+ 	the twisted affine dual of $J^1E$ 
  	\begin{displaymath}
@@
  	\end{displaymath}
- 	called \emph{"extended multiphase space"} and th twisted linear dual of $J^1 E$
+ 	called \emph{"extended multiphase space"} and the twisted linear dual of $J^1 E$
 	\begin{displaymath}
@@
 	called \emph{"standard multiphase space"} \footnote{$\LinDualJet$ can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}.\\
-	The first one can be also seen as an affine line bundle over the second one.
+	The first one can be also viewed as an affine line bundle over the second one.
 
-\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived by a multicanonical m-form $\theta$, obtained by pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
+\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived from a multicanonical $m$-form $\theta$, obtained by pulling back the tautological $m$-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
 	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.
 
-\item Dynamics can be implemented in two different way by fixing a further structure.\\
-	In the Lagrangian picture has to be fixed a bundle map:
+\item Dynamics can be implemented in two different ways by fixing a further structure.\\
+	In the Lagrangian picture one needs to fix a bundle map:
 	\begin{displaymath}
-		\Lagrangian : J^1 E \rightarrow \bigwedge^m (M)
+		\Lagrangian : J^1 E \rightarrow \wedge^m (M)
 	\end{displaymath}
-	, called \emph{Lagrangian density}, 	while in the Hamiltonian framework has to be fixed a section:
+	called \emph{Lagrangian density}, 	while in the Hamiltonian framework we fix a section:
 	\begin{displaymath}
@@
 
-\item Both of them determine a \emph{Legendre map}, computed as a fiber derivative, which allows us to move from one framework to another.
+\item Both of them determine a \emph{Legendre map}, computed as a fiber derivative, which allows us to move from one framework to the other.
 	Mainly we are interested  in the following:
@@
 	\end{displaymath}
-	The two dynamics function $\Lagrangian$ and $\Hamiltonian$ can be considered equivalent under the condition of \emph{hyper-regularity}\cite[chapter, p.~215]{Gimmsy}.
+	The two dynamical functions $\Lagrangian$ and $\Hamiltonian$ can be considered equivalent under the condition of \emph{hyper-regularity}\cite{Gimmsy}.
 
-\item Via $\mathbb{F} \Lagrangian$ we can pull-back the canonical forms on $J^1 E$ to give the \emph{Poincaré - Cartan forms} giving:
+\item We can pull-back the canonical forms on $J^1 E$ via $\mathbb{F} \Lagrangian$ to give the \emph{Poincaré - Cartan forms} reading:
 	\begin{displaymath}
@@
 	\end{displaymath}
-	Via $\Hamiltonian$ we can pull-back the canonical forms on $\LinDualJet$ to give the \emph{De Donder - Weyl forms} giving:
+	We can pull-back the canonical forms on $\LinDualJet$ via $\Hamiltonian$ to give the \emph{De Donder - Weyl forms} reading:
 	\begin{displaymath}
@@
 		\qquad 
-		\omega_\Hamiltonian = - \diff \theta_\Lagrangian
+		\omega_\Hamiltonian = - \diff \theta_\Hamiltonian
 	\end{displaymath}
 
-\item At last, can be introduced two map in order to encoded the field equations.
+\item At last, two map can be introduced in order to encode the field equations.
 	In the Lagrangian framework we consider the \emph{Euler-Lagrange map}
@@
 	\end{displaymath}
-	 a bundle-morphism acting on holonomic section submanifolds $\varphi(M)$ as:
+	 which is a bundle-morphism acting along holonomic sections:
 	\begin{displaymath}
@@
 	\end{displaymath}
-	 a bundle-morphism when evaluated on a vertical field $V$ on $E$.\\
+	 when evaluated on a vertical field $V$ on $E$.\\
 	In the Hamiltonian framework we consider the \emph{DeDonder-Weyl map}
@@
 	\end{displaymath}
-	acting on holonomic section submanifolds $(\varphi, \pi)(M)$ as:
+	which is a bundle-morphism acting along holonomic sections:
 	\begin{displaymath}
@@
 \item	
-	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-know motion equations when represented in local coordinate charts.
+	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-known equations of motion when represented in local coordinate charts.
 
@@
 The smooth bundle to be considered depends on the dynamical framework we are employing.
-We introduce the following notation, in order to treat both formalism at the same time:
+We introduce the following notation, in order to treat both formalisms at the same time:
 \begin{notation}
@@
 
-	\begin{definition}[Space of kinematics (off-shell) configurations]\label{Def:ConfSpace}
-		Is the, generally non-linear, infinte-dimensional manifold :
+	\begin{definition}[Space of kinematical (off-shell) configurations]\label{Def:ConfSpace}
+		It is the, generally non-linear, infinite-dimensional manifold :
 		\begin{displaymath}
@@
 		\end{displaymath}
-		so, we can equivalently consider holonomic jet sections of any order as the element of the configuration space.
+		so, we can equivalently consider holonomic jet sections of any order as elements of the configuration space.
 	\end{remark}	
@@
 	\begin{definition}[Space of Dynamics (on-shell) configurations]\label{Def:SolSpace}
-		Is the subset of $\Conf$:
+		It is the subset of $\Conf$:
 		\begin{displaymath}
@@
 		\end{displaymath}
-		containing all the smooth solutions of the motion equations corresponding to the  dynamical operator $D_\Lagrangian$ or $D_\Hamiltonian$ depending on the framework considered.
+		containing all smooth solutions of equation of motion corresponding to the  dynamical operator $D_\Lagrangian$ or $D_\Hamiltonian$, depending on the framework considered.
 	\end{definition}
 
-The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle composing with the jet functor $j$.
+The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the sections of a suitable vector bundle composing with the jet functor $j$.
 %
@@
 %
-The target base is a vector space, more precisely a frechet space \cite[Cap.2]{Ban} and makes sense to ask whetever $D_\cdot [\phi]$ is equal to the 0-section.
+The target base is a vector space, more precisely a Frechet space \cite[Cap.2]{Ban} and it makes sense to ask whether $D_\cdot [\phi]$ is equal to the 0-section.
 
-Again, we would like to employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
+Again, we employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
+%
 \begin{notation}
-	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend jet bundle over $F$ of different order, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
+	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on jet bundles over $F$ of different orders, a common notation on the multi-symplectic ground cannot be introduced directly
+	but we have to pass to the functional framework:
 \begin{displaymath}
@@
 \\
-	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
+	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results in:
 	\begin{displaymath}
@@
 
-	where has been employed the following correspondences:
+	where the following correspondences have been employed:
 	\begin{center}
@@
 	%
-	Noticing the recurring scheme we will also denote $	W = V^\TwistedLinear F $.
+	For brevity we will also set $	W = V^\TwistedLinear F $.
 \end{notation}
 
-Remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
-Natural beside the fact that its very structure, as a set, is expicitly determined by the fixed Lagrangian or Hamiltonian.\\
-Therefore, is the candidate to  be the field-theoretic (Covariant) phase space.
+A remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
+	It is "natural" modulo the fact that $\Sol$ is determined only once a Lagrangian or Hamiltonian has been chosen.
+\\
+ Therefore, $\Sol$ is the natural candidate for the field-theoretic (covariant) phase space.
 
@@
 
-Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as a manifold.
-Hence, we have to specify conveniently the structure of their tangent space in order to make clear the previous claim.
+Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as manifolds.
+Hence, we have to conveniently specify the structure of their tangent space in order to make the previous claim clear.
 
-The first thing to point out is the following chain of inequalities:
+The first thing to point out is the following chain of inclusions:
 \begin{displaymath}
@@
 This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
-Therefore, a parametrized regular curve as to be regarded as a family of diffeomerphisms, the flow generated by a vertical tangent field on $F$.\\
-The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.
+Therefore, a parametrized regular curve has to be regarded as a family of diffeomorphisms, the flow generated by a vertical tangent field on $F$.\\
+To consider the pull-back bundles stresses the fact that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$, that are vertical fields of $F$ \underline{along} the section $\phi$.
 \begin{notation}
@@
 In other words, it consists of the solutions of the \emph{Jacobi equations}.
-Rigourosly, this can be expressed in the following definition:
-	\begin{definition}[Tangent space to the Space of Solutions]\label{Def:TangentSol}
-		on a solution $\phi \in \Sol$, is the vector space
+Rigourosly, this can be expressed via the following definition:
+	\begin{definition}[Tangent space to the Space of Solutions on a solution $\phi \in \Sol$]\label{Def:TangentSol}
+		It is the vector space
 		\begin{displaymath}
@@
 \section{Jacobi Operator}\label{Sec:JacobiOperator}
-Intuitively, the Jacobi equation are the formal linearization of the motion equation around a solution $\phi$.\\
-Precisely they can be encoded in the following operator:
+Intuitively, the Jacobi equations are the formal linearization of the equation of motion around a solution $\phi$.\\
+Everything can be encoded in the following operator:
 %
@@
   \begin{minipage}[l]{0.5\textwidth}
-	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ target on the same space.
+	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ mapt to the same space.
   \end{minipage}
@@
 	around a solution $\phi$ when acting on an infinitesimal variation $\delta \phi \in T_\phi \Conf$
-	yields a twisted form that can be evaluated on any $V \in \Gamma\left(V F \right)$
+	via a twisted form that can be evaluated on any $V \in \Gamma\left(V F \right)$
 	yields the following expression:
@@
 \begin{proof}
-The explicit action of the Jacobi Operator can be reconstructed as follows:
+The explicit action of the Jacobi Operator can be expressed as follows:
 \begin{displaymath}
@@
 \begin{align*}
-	\left(J(\phi)\right) [\: ] (\cdot) =
+%	\left(J(\phi)\right) [\: ] (\cdot) =
 	\sigma \frac{\partial}{\partial \lambda} \eval{D[\phi_\lambda](\cdot)}_{\lambda=0}:
@@
 		\left. V_x \right\rangle =
-		\left\langle \left(J(\phi) \right) [\delta \phi] (x)
-		 \right\vert
-		\left. V_x \right\rangle =\\
-		&=
 		\left\langle\left.		
@@
 		\right\vert
-		 V_x \right\rangle =
+		 V_x \right\rangle = \\
+		 &=
 		 \eval{
@@
 	\end{displaymath}
-	recognizing that $\left(\phi_\lambda \cdot \phi_0^{-1}\right)$ is the flux generated by $\delta \phi$.
+	recognizing that $\left(\phi_\lambda \cdot \phi_0^{-1}\right)$ is the flow generated by $\delta \phi$.
 \end{proof}
@@
 \subsection{Construction of $\sigma$}\label{Section:sigma}
-Consider the two stacked bundle, $ W \rightarrow E$ vector bundle, $E \rightarrow M$ smooth bundle.
+Consider the two stacked bundles, $ W \rightarrow E$ vector bundle, $E \rightarrow M$ smooth bundle.
 	\begin{center}
-	  \includestandalone[mode=buildnew]{Pictures/Figure_ms_sigmaconstruction}
+	  \includestandalone{Pictures/Figure_ms_sigmaconstruction}
 	\end{center}
@@
 
-We have the following short exact sequence of bundle morphism over $W$:
+We have the following short exact sequence of bundle morphisms over $W$:
 	\begin{center}
@@
 \end{displaymath}
-so, by splitting lemma, we have a left splitting $\sigma : B \rightarrow A$ that is exactly the searched operator.
+so, by splitting lemma, we have a left splitting $\sigma : B \rightarrow A$ that is exactly the desired operator.
 
@@
 \end{displaymath}
-which determine an intrinsic mapping 
+which determines an intrinsic mapping 
 \begin{displaymath}
@@
 
-Since we have such projection for all $e \in E$ and it acts fiberwise, it can be regarded as a bundle morphism over $E$:
+Since this projection is defined for all $e \in E$ and it acts fiberwise, it can be regarded as a bundle morphism over $E$:
 \begin{displaymath}
@@
   \centering
-	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaAction}
+	\includestandalone[width=0.85\linewidth]{Pictures/Figure_sigmaAction}
  \\ \small{general case}
@@
  Roughly, the strategy of construction is the following:
+
+	\begin{center}
+		\includestandalone[width=0.80\linewidth]{Pictures/Figure_symformidea}
+	\end{center}
+%
+	\begin{itemize}
+		\item Consider $\phi \in \Conf$ and 
+		a pair of variations $\delta \phi_1 , \delta \phi_2 \in T_\phi \Conf$.
+		\item Find a way to contract $\delta \phi$ and $\delta \phi '$ , seen as tangent vector field on $E$, with the multi-symplectic forms $\omega$.
+		\item Pull-back the obtained $m-1$ form to $M$, oriented manifold.
+		\item Integrate thus form on a suitable $(m-1)$ dimensional sub-manifold of $M$.
+		\item Take the resulting number as the evaluation of the desired form on the two variations.  
+	\end{itemize}
+
 	\vspace{0.5cm}
-
-  \begin{minipage}[l]{0.5\textwidth}
-	\includegraphics[width=\textwidth]{Pictures/symform.png}
-  \end{minipage}\hfill
-  \begin{minipage}[r]{0.45\textwidth}
-	\begin{itemize}
-		\item Find a way to contract $\delta \phi$ and $\delta \phi '$ , seen as tangent vector field on $E$, with the multi-symplectic forms $\omega$.
-		\item pull-back the obtained $m-1$ form to $M$, oriented manifold.
-		\item Integrate thus form on a suitable $(m-1)$ dimensional sub-manifold of $M$.
-		\item take the resulting number as the evaluation of the desired form on the two variations.  
-	\end{itemize}
-  \end{minipage}\hfill
-
-  	\vspace{1cm}
-
 Rigourosly, fixed  $\Sigma$, a compact $m-1$ dimensional submanifold of $M$, we define:
@@
 		\int_\Sigma (\phi)^\ast \left[ i_{\delta\phi_2} i_{\delta \phi_1} \omega \right] =
-		\int_\Sigma \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right) = 
-		\begin{cases}
-			\int_\Sigma (j^1 \varphi)^\ast \left[ i_{j^1 \delta\varphi_2} i_{j^1 \delta \varphi_1} \omega_\Lagrangian \right]
-			\\
-			\int_\Sigma (\varphi, \pi)^\ast \left[ i_{( \delta \varphi_2, \delta \pi_2)} i_{( \delta \varphi_1, \delta \pi_1)} \omega_\Hamiltonian \right]	
-		\end{cases}
+		\int_\Sigma \Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right)
 	\end{displaymath}
-where the form $\Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right)  \in \Omega^{m-1}(M)$ to be integred on $\Sigma$ is called \emph{Symplectic current}.
+where the form $\Upsilon_\phi \left( \delta \phi_1 , \delta \phi_2 \right)  \in \Omega^{m-1}(M)$ to be integrated on $\Sigma$ is called \emph{Symplectic current}.
 \end{definition}
@@
 
-The form $\Omega_\Sigma (\phi)$ is manifestly bilinear and skew-symmetric but it is far from obvious, at this stage, to prove exactness and non-degeneracy.
-We can not conclude yet that it is a symplectic form.
-However, the clumsy dependence from the choice $\Sigma$ represent a more urgent problem.
-An important remark can be done:
+The form $\Omega_\Sigma (\phi)$ is manifestly bilinear and skew-symmetric but it is far from obvious, at this stage, to prove closure and non-degeneracy.
+We cannot conclude yet that it is a symplectic form.
+However, the clumsy dependence from the choice of $\Sigma$ represents a more compelling problem.
+An important remark is the following:
 
@@
 	\end{displaymath}
-	and $V_i$ are solution of the Jacobi equation.\\
-	The last term vanishes since the lie bracket of two vertical vector field along $\phi$ is equal to the brackets of two vertical field over $F$ constant on each fiber.
+	and $V_i$ are solutions of the Jacobi equation.\\
+	The last term vanishes since the Lie bracket of two vertical vector field along $\phi$ is equal to the brackets of two vertical fields over $F$ which are constant on each fiber.
 \end{proof}
@@
 However, it is not sufficient to eliminate the unwanted dependence from the choice of $\Sigma$.
-In order to get rid of this drawback is necessary to introduce some other assumptions.\\
-It is customary to require the working condition of physical field system theories on curved background\cite{primer}:
+In order to get rid of this drawback it is necessary to introduce some other assumptions.\\
+It is customary to require the following working condition of physical field system theories on curved background
+\cite{primer}:
 \begin{enumerate}
 	\item $M$ is a \emph{globally-hyperbolic spacetime}
-	\item $\Sigma$ is an arbitrary cauchy surface
+	\footnote{Oriented, time-oriented, connected, Lorentzian smooth manifold. } 
+	\item $\Sigma$ is an arbitrary Cauchy surface
 	\item $T_\phi \Conf =\Gamma_{sc} (V^\TwistedLinear F )$ i.e. are only considered space-like compact variations.
@@
 %
-Considering a spacetime \footnote{Oriented, time-oriented, connected, Lorentzian smooth manifold. } allow us to define a space-like compact support.\\
-So, the first condition guarantees that exists a Cauchy surface and that the spacetime can be foliated according to it $M= \Sigma \times \Real$.\\
-Whereas, from the last condition, follows that for any Cauchy surface $\Sigma$, $ \supp(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \cap \Gamma$ is compact, thus the integration involved in definition \ref{Def:presymform} is always well-defined.
+%Considering a spacetime allow us to define a space-like compact support.\\
+So, the first condition guarantees that there exists a Cauchy surface and that the spacetime can be foliated as $M= \Sigma \times \Real$.\\
+The last condition, implies that for any Cauchy surface $\Sigma$, $ \supp(\Upsilon_\phi (\delta \phi_1, \delta \phi_2) \cap \Gamma$ is compact, hence the integration involved in definition \ref{Def:presymform} is always well-defined.
 
 \begin{proposition}
-	In this condition $\Omega_\Sigma (\phi): T_\phi \Sol \times T_\phi \Sol \rightarrow \Real$ does not depends on the choice of $\Sigma$ anymore.
+	In the above conditions, $\Omega_\Sigma (\phi): T_\phi \Sol \times T_\phi \Sol \rightarrow \Real$ does not depend on the choice of $\Sigma$.
 \end{proposition}
@@
 	\end{displaymath}
-	by varying $t$, it determines an m-dimensional domain $V \subset M$.
-	For any $U$ open set in $M$ containing $K={K_t}_{0<t<t'}$ we have, as a simple consequence of proposition \ref{Prop:CurrentClosed} and Stokes' lemma, that
+	by varying $t$, it determines an $m$-dimensional domain $V \subset M$.
+	For any $U$ open set in $M$ containing $K={K_t}_{0<t<t'}$ we have, as a simple consequence of Proposition \ref{Prop:CurrentClosed} and Stokes' lemma, that
 	\begin{displaymath}
@@
 %
-Dynamics is encoded into the Hamiltonian density $H$:
+The dynamics is encoded into the Hamiltonian density $H$:
 \begin{displaymath}
@@
 %
-De Donder-Weyl forms are obtained from the tautological form on $\AffDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A, p)$
+The De Donder-Weyl forms are obtained from the tautological form on $\AffDualJet \rightsquigarrow (x^\mu, q^A, p^\mu_A, p)$
 \begin{displaymath}
@@
 \end{displaymath}
-and external derivation
+and exterior derivation
 \begin{displaymath}
@@
 \end{align*}
-where $(\varphi, \pi)$ has to be intended as $\left(x^\mu, \varphi^A(x), \pi^\mu_A(x)\right)$.
+where $(\varphi, \pi)$ is an abridged notation for $\left(x^\mu, \varphi^A(x), \pi^\mu_A(x)\right)$.
 %
@@
 \end{displaymath}
-can be explicitly computed the directional derivative of the map
+the directional derivative of the map can be explicitly computed 
 \begin{align*}
@@
 \end{align*}
-where the last two terms determine an explicit expression for the Jacobi operator in the case that $(\varphi,\pi)$ is a solution of the motion equations:
+where the last two terms yield the Jacobi operator when $(\varphi,\pi)$ is a solution of the equations of motion:
 \begin{align*}
@@
 where $\diff \sigma_\mu $ is the induced volume form on $\Sigma$ from $M$.\\
-Furthermore the external derivative of the form results:
+Furthermore the external derivative of the reads:
 \begin{align*}
@@
 \end{align*}
-In the case that $(\delta \varphi_i, \delta \pi_i) \in T_{(\varphi,\pi)}\Sol$ we can plug equations \ref{Eq.:Jacobi} in the latter expression giving
+In the case that $(\delta \varphi_i, \delta \pi_i) \in T_{(\varphi,\pi)}\Sol$ we can plug equations \ref{Eq.:Jacobi} in the latter expression, obtaining
 \begin{align*}
@@
 \end{align*}
-thus proving the closedness of the symplectic current.
+thus proving the closure of the symplectic current.
 

### 2017-06-13 Pictures/Figure_Jacobi.tex
New picture on the convariant approach.

\documentclass[border=10pt, tikz]{standalone}

\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}

%Funzione 3D
\pgfmathdeclarefunction{F}{2}{\pgfmathparse{exp(-(#1^2+#2^2))}}
%{\pgfmathparse{3000-1000*sin(#1)+1500*(#2/6)^5}}
%*(#2/6)^3

%Common symbols
\usepackage[multisym, geomec, basic, diffgeo]{../Math-Symbols-List/toninus-math-symbols}

\begin{document}
\begin{tikzpicture}
\begin{axis}[axis lines=none,clip=false,view={30}{45},]

	%Spazio Delle Configurazioni Cinematiche
	\addplot3[ domain=-1:1,y domain=-1:1,
					 colormap/greenyellow, opacity=0.1,fill opacity=0.5,
					 surf,    
					 ]
	{F(x,y)};

	%Phi0$
	\node[pin={135:{ $\phi$}},circle,fill,inner sep=1pt] at (axis cs:0,0,{F(0,0)}) {};
  	\node[pin={-30:{$\Conf = \Gamma^\infty(F,M)$}}]  at (axis cs:0.9,0,{F(0.9,0)}) {};
   	\node[pin={[blue]80:{$ T_\phi\Conf \subseteq  \Gamma^\infty\left( \phi^\ast (VF) \right)$}}] at (axis cs:-0.2,0.8,1) {};

	% Curve parametrizzate sulla superficie (le spezzo a metà così riesco a mettere bene il vettore tangente
		\addplot3[red,opacity=0.5,domain=0:2,variable=\t,samples y=0] ({-1+t},{-1+t},{F(-1+t,-1+t)})
			node[pin={30:{$\Sol= \ker(D[\;])$}}]{};

	% Tangent conf
	  \draw[blue,fill=blue!5,opacity=.50] (0.9,-0.9,1) -- (0.9,0.9,1) -- (-0.9,0.9,1) -- (-0.9,-0.9,1) -- cycle;

	%Tangent Sol
		\draw[orange] (-0.9,-0.9,1) -- (0.9,0.9,1) node[pin={30:{$T_{\phi}\Sol = \ker(J_\phi[\;])$}}]{};

	\node(target) [rectangle, rounded corners, draw=black,fill=gray!5,
                  text centered,
                  minimum width=5cm, minimum height=1cm,] 
                  at (0,0,3){$\Gamma^\infty ( V^\TwistedLinear F)$};

  	\draw[->]	(-1,-0.6,{F(-1,-0.6)}) edge[bend left=70] node [left] {$D [\;]$} (target.west);
  	\draw[->,blue]	(-0.9,-0.5,1) edge[bend left=30] node [ left] {$J_\phi [\;]$} (target.south west);

\end{axis}
\end{tikzpicture}
\end{document}

### 2017-06-13 cpsviams.tex
New picture on the convariant approach.

@@
 %
-  \begin{minipage}[r]{0.5\textwidth}
-    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
+  \begin{minipage}[r]{0.80\textwidth}
+  	\includestandalone[width=0.85\textwidth]{Pictures/Figure_Jacobi}
+    %\includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
   \end{minipage}\hfill
-  \begin{minipage}[l]{0.5\textwidth}
-	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ mapt to the same space.
+  \begin{minipage}[l]{0.20\textwidth}
+	Note that $ \left(J(\phi)\right) [ \; ]$ and $D[\;]$ maps to the same space.
   \end{minipage}
 
+\vspace{5mm}
 Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $, that is also vertical w.r.t. $M$, 

### 2017-06-16 cpsviams.tex
Little comment on vector bundles over Conf space.

--- 2017-05-31 cpsviams.tex
@@
 %
-The target base is a vector space, more precisely a Frechet space \cite[Cap.2]{Ban} and it makes sense to ask whether $D_\cdot [\phi]$ is equal to the 0-section.
+The target base is a vector space, more precisely a Frechet space \cite[Cap.2]{Ban}, and it makes sense to ask whether $D_\cdot [\phi]$ is equal to the 0-section.
 
@@
 %
-  \begin{minipage}[r]{0.5\textwidth}
-    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
-  \end{minipage}\hfill
-  \begin{minipage}[l]{0.5\textwidth}
-	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ mapt to the same space.
-  \end{minipage}
+	Note that $D[ \phi]$  and $ \left(J(\phi)\right) [ \delta \phi ]$  $(\forall \delta\phi \in T_\phi\Conf)$ are vectors in the same vector space.
+	%
+	Considering the "formal" infinite dimensional vector bundle 
+	\begin{displaymath}
+		\mathcal{E} =\bigsqcup_{\phi \in \Conf} 
+			\Gamma^\infty \left( 
+				\phi^\ast(V^\TwistedLinear F)
+			\right)
+			\rightarrow \Conf
+	\end{displaymath}
+	$D$ could be regarded as a section on it and $J$ as a bundle map from $T\Conf$ to $V\mathcal{E}\simeq \mathcal{E}$.
+	\begin{center}
+	  	\includestandalone[width=0.85\textwidth]{Pictures/Figure_Jacobi}
+	\end{center}
 
@@
 		\end{displaymath}
-		because $D[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$.
+		because $D[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$.\\
 		Hence the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
@@
 	around a solution $\phi$ when acting on an infinitesimal variation $\delta \phi \in T_\phi \Conf$
-	via a twisted form that can be evaluated on any $V \in \Gamma\left(V F \right)$
-	yields the following expression:
+	gives a twisted form that can be evaluated on any $V \in \Gamma\left(V F \right)$
+	yielding the following expression:
 	\begin{displaymath}	
@@
 %
-\begin{eqnarray*}
-	\ker(i) = 0 (E) = i' \left( 0 \right)
-	\ker\left( T \pi_{E,W} \right) = V_E W = i\left( V_E W \right)
-	\ker\left(T \pi_{M,E}\right) = V_M E = T \pi_{E,W} \left( V_M W \right)
-\end{eqnarray*}
+\begin{align*}
+	&\ker(i) = 0 (E) = i' \left( 0 \right) \\
+	&\ker\left( T \pi_{E,W} \right) = V_E W = i\left( V_E W \right) \\
+	&\ker\left(T \pi_{M,E}\right) = V_M E = T \pi_{E,W} \left( V_M W \right) \\
+\end{align*}
 
+%
 We can exhibit a right splitting, that is:
@@
 Therefore, we have the following decomposition:
-
+%
 \begin{displaymath}
@@
 \end{align*}
-thus proving the closure of the symplectic current.
+thus the closure of the symplectic current is verified.
 

### 2019-02-18 ms-mechanics.tex
Kickstarting new Section

\title{(An introduction to )MultiSymplectic Geometry and Classical Field systems}
\author{
	International Ph.D. Program in "Science" \\
	"Differential geometry and applications to modern physics" \\
	Department of Mathematics and Physics\\
	Universit\'a Cattolica del Sacro Cuore\\
	via Musei 41, 25121 Brescia, \underline{Italy}
}

\documentclass[a4paper,12pt,fleqn]{scrartcl}  %Per La Stampa
\usepackage[a4paper, margin=2cm]{geometry}

\usepackage{amsmath}
\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
\usepackage[subpreambles=true]{standalone}
\usepackage{commath}

\usepackage[italian,english]{babel}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{hyperref}

%\usepackage{Latex-Theorem/theoremtemplate}

%	\renewcommand{\AffDualJet}{ J^{1 \TwistedAffine}E }
%	\renewcommand{\LinDualJet}{ \overrightarrow{J^{1 \TwistedLinear}E} }

\begin{document}
\maketitle

\begin{abstract}
$n$-plectic structures (also called \emph{multisymplectic}) are a rather straightforward generalization of symplectic ones where closed non-degenerate $n+1$-forms take the place of  $2$-forms.
\\
As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g. a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium as a filament or a membrane).
\\
The aim of my talk is to give an account on the multisymplectic framework for (I-order) classical fields theories comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
\\
Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.

\end{abstract}

%------------------------------------------------------------------------------------------------
% Bibliography (BibTex)
% https://arxiv.org/hypertex/bibstyles/
%------------------------------------------------------------------------------------------------
			\nocite{*}
			\bibliographystyle{ieeetr}
			\bibliography{biblio}
%------------------------------------------------------------------------------------------------

\subsection{Far capire cosa intendo per campo classico}
Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
\begin{table}[]
\begin{tabular}{lll}
	System & Configuration space (locally) & protoype 
 	\\
	Ordinary system & $\mathbb{R}^n$ with $n\in \mathbb{N} = Hom_{set}(\{1,\ldots n\}, \mathbb{R})$ & A point on a $n$-dimensional mfd.
	\\
	1 dimensional field & $\mathbb{R}^\mathbb{R} = C^\infty(\mathbb{R},\mathbb{R})$ & collection of points on a line each one parametrized by ...
	\\
	n dimensional field & $(\mathbb{R}^m)^{\mathbb{R}^n} = C^\infty (\mathbb{R}^n, \mathbb{R}^m)$ & ...
\end{tabular}
\end{table}

\subsection{spunti Open problems}
	We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?

	We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?

\section{Spunti dei Saggi}
\subsection{Rogers: arXiv:1009.2975v3}
Multisymplectic manifolds naturally arise in certain covariant Hamiltonian formalisms for classical field theory.
In these formalisms, one describes a $(n+1)$-dimensional field theory by using a finite-dimensional $n$-plectic manifold as a \emph{multi-phase space} instead of an infinite-dimensional phase space. 
The $n$-plectic form can be used to define a system of partial differential equations which are the analogue of Hamilton's equations in classical mechanics. 
The solutions to these
equations correspond to particular submanifolds of the multi-phase space that encode the value of the field at each point in space-time as well as the values of its time and spatial derivatives.

\end{document}

### 2019-02-22 ms-mechanics.tex
Starting new lectures notes (Multisymplectic)

@@
 
-\documentclass[a4paper,12pt,fleqn]{scrartcl}  %Per La Stampa
-\usepackage[a4paper, margin=2cm]{geometry}
+\documentclass[a4paper,12pt,fleqn]{article}  %Per La Stampa
+\usepackage[a4paper, margin=3cm]{geometry}
 
@@
 
+\providecommand{\oast}{\ensuremath{\:\!%
+ {\raisebox{0.1ex}{$\scriptscriptstyle \bigcirc$} \hspace{-0.5em} \ast}}}
+\providecommand{\ostar}{\ensuremath{\:\!%
+ {\raisebox{0.05ex}{$\scriptscriptstyle \bigcirc$} \hspace{-0.5em} \star}}}
+\providecommand{\smoast}{\ensuremath{%
+ {\raisebox{-0.25ex}{$\textstyle \circ$} \hspace{-0.42em}
+ {\scriptscriptstyle \ast}}}}
+\providecommand{\smostar}{\ensuremath{%
+ {\raisebox{-0.25ex}{$\textstyle \circ$} \hspace{-0.42em}
+  \raisebox{0.05ex}{$\scriptscriptstyle \star$}}}}
+
 \begin{document}
 \maketitle
+
+$$
+\ast 
+\star 
+\oast 
+\ostar
+\smoast
+\smostar
+J^\smostar
+J^\smoast
+J^\ostar
+$$
 
@@
 As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g.
-a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium as a filament or a membrane).
+a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium like a filament or a membrane).
 \\
@@
 \\
-Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.
+Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.
 
@@
 
-\subsection{Far capire cosa intendo per campo classico}
+\section{A glance at the geometric approach to classical mechanics}
+Recall: Geometric Mechanics of Classical system
+Configuration space
+Generalized velocities space and phase space
+...
+
+\section{Far capire cosa intendo per campo classico}
 Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
@@
 
-\subsection{spunti Open problems}
-	We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+A questo punto si dovrebbe Essere chiaro il punto di partenza:
+\\
 
-	We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
+\section{Kinematics of Classical fields}
+The starting point is the \emph{configuration bundle} 
+ 	\begin{displaymath}
+ 		E = \left( \pi_{M,E} : E\rightarrow M \right)
+ 	\end{displaymath}
+is a smooth bundle encoding the kinematics.
+
+\subsection{Jet Bundle}
+The first jet bundle of $E$ generalises the space of generalized velocities.
+
+The fiber over a point $y\in E$ is
+\begin{displaymath}
+	\left( J^1 E\right)_y = \left\lbrace \gamma \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ \gamma = \text{id}_{T_{\pi(x)} M} \right\rbrace
+\end{displaymath}
+(T = Tangent functor L = space of linear maps)
+
+which is and affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
+\begin{displaymath}
+	\vec{\left( J^1 E\right)_y} = \left\lbrace z \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ z = 0 \right\rbrace
+	\cong text{L}(T_{\pi(y)}M, T_y E)
+\end{displaymath}
+
+\section{Spunti / Open problems}
+\begin{itemize}
+	\item We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+	\item We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
+	\item there are other notion of moment map on the multisymplectic setting. For instance how the definition in section 4 of \cite{Gotay1998a} is related to the one in \cite{Ryvkin2018}?
+\end{itemize}
 
@@
 
+\subsection{Forger-Romero}
+The two formalisms, although both fully covariant and directed towards
+the same ulti\-mate goal, are of different nature; each of them has its
+own merits and drawbacks.
+\begin{itemize}
+ \item The multisymplectic formalism is manifestly consistent with the
+       basic principles of field theory, preserving full covariance, and
+       it is mathematically rigorous because it uses well established
+       methods from calculus on finite-dimensional manifolds. On~the
+       other hand, it does not seem to permit any obvious definition
+       of the \mbox{Poisson} bracket between observables. Even the
+       question of what mathematical objects should represent physical
+       observables is not totally clear and has in fact been the subject
+       of much debate in the literature. Moreover, the introduction of
+       $n$ conjugate momenta for each coordinate obscures the usual
+       duality between canonically conjugate variables (such as momenta
+       and positions), which plays a fundamental role in all known methods
+       of quantization. A definite solution to these problems has yet to be
+       found.
+ \item The covariant functional formalism fits neatly into the philosophy
+       underlying the symplectic formalism in general; in particular, it
+       admits a natural definition of the Poisson bracket (due to Peierls
+       \cite{Pe} and further elaborated by DeWitt \cite{DW1,DW2,DW3})
+       \linebreak that preserves the duality between canonically conjugate
+       variables. Its main drawback is the lack of mathematical rigor, since
+       it is often restricted to the formal extrapolation of techniques from
+       ordinary calculus on manifolds to the infinite-dimensional setting:
+       transforming such formal results into mathematical theorems is a
+       separate problem, often highly complex and difficult.
+\end{itemize}
+
+Multiphase space (ordinary as well as extended) is the geometric environment
+built by appropriately patching together local coordinate systems of the form
+$(q^i,p\>\!_i^\mu)$~-- in- \linebreak stead of the canonically conjugate
+variables $(q^i,p_i)$ of mechanics~-- together with space-time coordinates
+$x^\mu$ and, in the extended version, a further energy type variable that
+we shall denote by $p$ (without any index). The global construction of
+these multiphase spaces, however, has only gradually come to light; it
+is based on the following mathematical concepts.
+\begin{itemize}
+ \item The collection of all fields in a given theory, defined over a fixed
+       ($n$-dimensional orientable) space-time manifold $M$, is represented
+       by the sections $\varphi$ of a given fiber bundle $E$ over $M$, with
+       bundle projection $\, \pi : E \rightarrow M \,$ and typical fiber $Q$.
+       This bundle will be referred to as the \emph{configuration bundle}
+       of the theory since $Q$ corresponds to the configuration space of
+       possible field values.
+ \item The collection of all fields together with their partial derivatives
+       up to a certain order, say order $r$, is represented by the $r$-jets
+       $\, j^{\,r\!} \varphi \equiv (\varphi,\partial\varphi,\ldots,
+       \partial^{\,r\!} \varphi)$  of sections of $E$, which are
+       themselves sections of the $r^{\mathrm{th}}$ order jet bundle
+       $J^r E$ of $E$, regarded as a fiber bundle over~$M$. In this paper,
+       we shall only need first order jet bundles, \linebreak with one
+       notable exception: the global formulation of the Euler\,-\,Lagrange
+       equations requires introducing the second order jet bundle.
+ \item Dualization -- the concept needed to pass from the Lagrangian to
+       the Hamiltonian framework via the Legendre transformation -- comes
+       in two variants, based on the fundamental observation that the first
+       order jet bundle $J^1 E$ of $E$ is an affine bundle over $E$ whose
+       difference vector bundle $\vec{J}^{\,1} E$ will be referred to as
+       the linear jet bundle. Ordinary multiphase space is obtained as
+       the twisted linear dual $\vec{J}^{\,1\oast} E$ of $\vec{J}^{\,1} E$
+       while extended multiphase space is obtained as the twisted affine
+       dual $J^{1\ostar} E$ of $J^1 E$, where the prefix ``twisted'' refers
+       to the necessity of taking an additional tensor product with the
+       bundle of $n$-forms on $M$.\footnote{We use an asterisk $\ast$ to
+       denote linear duals of vector spaces or bundles and a star $\star$
+       to denote affine duals of affine spaces or bundles. These symbols
+       are appropriately encircled to characterize twisted duals, as
+       opposed to the ordinary duals defined in terms of linear or
+       affine maps with values in $\mathbb{R}$.}
+ \item The Lagrangian $\mathcal{L}$ is a function on $J^1 E$ with values
+       in the bundle of $n$-forms on~$M$ so that it may be integrated to
+       provide an action functional which enters the variational principle.
+       The De Donder\,-\,Weyl Hamiltonian $\mathcal{H}$ is a section of
+       $J^{1\ostar} E$, considered as an affine line bundle over
+       $\vec{J}^{\,1\oast} E$.
+\end{itemize}
+Note that the formalism is set up so as to require no additional structure
+on the con\-figuration bundle or on any other bundle constructed from it:
+all are merely fiber bundles over the space-time manifold $M$. Of course,
+additional structures do arise when one is dealing with special classes
+of fields (matter fields and the metric tensor in general relativity are
+sections of vector bundles, connections are sections of affine bundles,
+nonlinear fields such as those arising in the sigma model are sections
+of trivial fiber bundles with a fixed Riemannian metric on the fibers,
+etc.), but such additional structures depend on the kind of theory
+considered and thus are not universal. Finally, the restriction
+imposed on the order of the jet bundles considered reflects the
+fact that almost all known examples of field theories are governed by
+second order partial differential equations which can be derived from a
+Lagrangian that depends only on the fields and their partial derivatives
+of first order, which is why it is reasonable to develop the general
+theory on the basis of a first order formalism, as is done in mechanics
+\cite{AM,Arn}.
+
+A fundamental prerequisite for setting up a general mathematical framework
+for geo\-metric field theory is to obtain a clear picture of what should be
+the most general concept of a (classical) field. In physics, we distinguish
+basically four different types of fields.
+\begin{itemize}
+ \item \emph{Matter fields} are fields that, in the context of quantum theory
+       and in particular of the standard model, are associated with particles
+       that constitute matter -- quarks and leptons.
+ \item \emph{Gauge fields} are fields that, in the context of quantum theory
+       and in particular of the standard model, are associated with particles
+       that mediate three of the four fundamental interactions: the photon
+       $\gamma$ for the electromagnetic interaction, the three intermediate
+       vector bosons $W^\pm$ and $Z^0$ for the weak interaction and the
+       eight gluons for the strong interaction. Among the three, only
+       one -- the electromagnetic interaction -- describes a long-range
+       force and therefore plays an important role also in the macroscopic
+       world, where it is governed by Maxwell's theory of electromagnetism.
+ \item \emph{Gravitational fields} occupy a particular position because
+       according to general relativity as formulated by Einstein, they
+       are related to the metric properties of space-time itself.
+       Historically, general relativity has been the first example
+       of a geometric field theory.
+ \item \emph{Nonlinear fields} are fields taking values in some nonlinear
+       manifold, often obtained as a submanifold of some vector space.
+       Typical examples are the Heisenberg model (the continuum limit
+       of the Heisenberg spin chain) and the sigma model.
+\end{itemize}
+Obviously, a general mathematical formalism for classical field theory
+should be based on concepts capable of accomodating all these types of
+fields. This leads to the definition of a field as being a section of
+a (general) fiber bundle~$E$ over space-time~$M$, without additional
+structure, since different types of fields correspond to sections of
+different types of fiber bundles.
+\begin{itemize}
+ \item \emph{Matter fields} are sections of some given vector bundle over $M$,
+       built from the tangent bundle $TM$ of $M$ together with its descendants
+       (to accomodate the tensorial or spinorial character of these fields)
+       and possibly from vector bundles $V$ over $M$ associated to some
+       principal bundle $P$ over $M$ whose structure group describes
+       internal symmetries.
+ \item \emph{Gauge fields} are usually defined as connection forms on the
+       total space of some given principal bundle $P$ over $M$ but can be
+       reinterpreted as sections of the connection bundle of $P$ -- an
+       affine bundle $CP$ over $M$ constructed canonically from $P$.
+       See for example \cite{NODG}.
+ \item \emph{Gravitational fields} are traditionally described by a metric
+       tensor which, again, is a section of a vector bundle over $M$, namely
+       the symmetric second tensor power of the cotangent bundle $T^* M$ of
+       $M$, but subject to the condition of non-degeneracy and Lorentzian
+       signature which restricts it to take values in a certain open
+       subbundle of the latter.
+ \item \emph{Nonlinear fields} are usually sections of a globally trivial
+       bundle $\, E = M \times Q \,$ where $Q$ is a given manifold; such
+       sections can be identified with maps from $M$ to $Q$. In the most
+       general version of the sigma model, $Q$ is just a Riemannian manifold.
+\end{itemize}
+
+\nocite{*}
+\bibliographystyle{alpha}
+\bibliography{biblio}
+
 \end{document}

### 2019-03-01 ms-mechanics.tex
Updating after talk in Leuven

--- 2019-02-18 ms-mechanics.tex
@@
 
-%------------------------------------------------------------------------------------------------
-% Bibliography (BibTex)
-% https://arxiv.org/hypertex/bibstyles/
-%------------------------------------------------------------------------------------------------
-			\nocite{*}
-			\bibliographystyle{ieeetr}
-			\bibliography{biblio}
-%------------------------------------------------------------------------------------------------
+\section{Preliminiaries}
 
-\subsection{Far capire cosa intendo per campo classico}
+%What's geometric Mechanics
+\subsection{A glance at the geometric approach to classical mechanics}
+The context in which we are going to work is \emph{Geometric Mechanics}.
+\\
+Roughly speaking, geometric mechanics is a branch of (applied) mathematics that employs differential geometry to the description of physical systems.
+Unlike analytical mechanics, the focus is on encoding the mechanical properties of a physical system regardless of the reference frame (coordinate system).
+\\
+Let us briefly recall what are the most important ingredients of an ordinary classical\footnote{Here "ordinary" stands for finite degrees of freedom and "classical" stands for non-quantum and non-relativistic.} system.
+
+\begin{center}
+  %\includestandalone{Pictures/Figure_ordinary_landscape}
+\end{center}
+
+\begin{itemize}
+	\item The starting point is the \emph{Configuration space}, that is a smooth manifolds $Q$ containing all possible spatial displacements of a system.\\
+	E.g. for the simple planar pendulum $Q= S^1$, for a double pendulum $Q =\mathbb{T}^2$
+	\item A point in $Q$ is a statical configuration, that is opposed to the elements of the \emph{space of kinematics configuration}
+	$$ \mathcal{C} = C^\infty(\mathbb{R},Q)$$
+	which is the collection of all trajectories admitted by the constraints.
+	\item The tangent bundle $TQ$ takes the name of \emph{space of generalized velocities}
+	\item The cotangent bundle $T^\ast Q$ is called \emph{phase space}.
+Such space carries a natural symplectic form $\omega$ (\emph{Poincare\'} 2-form) defined in term of the tautological 1-form $$\omega= \text{d} \theta$$
+\end{itemize}
+%
+All of this encode the geometry of the kinematics.
+Fixing a point in the previous two spaces is tantamount to give a complete set of initial data determining unambiguously the evolution of the system.
+\\
+Such point carries more information that the simple spatial displacement and are interpreted as the \emph{physical state} of the system.
+%
+\begin{itemize}
+\item Dynamics is encoded by two smooth functions:
+	\\ 
+	$L:TQ\rightarrow \mathbb{R}$ in the \emph{Lagrangian} framework
+	\\
+	$H:T^\ast Q \rightarrow \mathbb{R}$ in the \emph{Hamiltonian} framework
+	\\
+	Generally the two framework are not equivalent.
+\item From the Lagrangian $L$ or the Hamiltonian $H$ one can obtain the so-called \emph{Action functional} $S:\mathcal{C}\rightarrow \mathbb{R}$ which yields the equation of motion through the d'Alambert principle.
+\end{itemize}
+%
+The goal of this talk is to describe the analogue of this framework in the case of classical field systems.
+
+%What's a Classical Field
+\subsection{Modelling a classical field theory}
+A classical field theory is a physical theory that predicts how "physical fields" evolves according to their interaction with the matter and themselves.
+\\
+The term "classical" is commonly reserved to theories treating electro-magnetism and gravitation. Here it is meant as non-quantum mechanics of physical fields or continuous systems.
+
+Roughly, a physical field can be thought as the assignment of a physical quantity at each point of space and time.
+
 Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
@@
 
-\subsection{spunti Open problems}
-	We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+A questo punto si dovrebbe Essere chiaro il punto di partenza:
+\\
 
-	We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
+\subsection{Multisymplectic geometry}
 
-\section{Spunti dei Saggi}
-\subsection{Rogers: arXiv:1009.2975v3}
-Multisymplectic manifolds naturally arise in certain covariant Hamiltonian formalisms for classical field theory.
-In these formalisms, one describes a $(n+1)$-dimensional field theory by using a finite-dimensional $n$-plectic manifold as a \emph{multi-phase space} instead of an infinite-dimensional phase space. 
-The $n$-plectic form can be used to define a system of partial differential equations which are the analogue of Hamilton's equations in classical mechanics. 
-The solutions to these
-equations correspond to particular submanifolds of the multi-phase space that encode the value of the field at each point in space-time as well as the values of its time and spatial derivatives.
+\section{Multymplectic approach to classical field theories}
+Tabella -Dictionary
+
+\subsection{Configuration Bundle}
+-Kinematics of Classical fields-
+The starting point is the \emph{configuration bundle} 
+ 	\begin{displaymath}
+ 		E = \left( \pi_{M,E} : E\rightarrow M \right)
+ 	\end{displaymath}
+is a smooth bundle encoding the kinematics.
+
+\subsection{Jet Bundle}
+The first jet bundle of $E$ generalises the space of generalized velocities.
+
+The fiber over a point $y\in E$ is
+\begin{displaymath}
+	\left( J^1 E\right)_y = \left\lbrace \gamma \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ \gamma = \text{id}_{T_{\pi(x)} M} \right\rbrace
+\end{displaymath}
+(T = Tangent functor L = space of linear maps)
+
+which is and affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
+\begin{displaymath}
+	\vec{\left( J^1 E\right)_y} = \left\lbrace z \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ z = 0 \right\rbrace
+	\cong text{L}(T_{\pi(y)}M, T_y E)
+\end{displaymath}
+
+\subsection{Dualization of Jet bundles}
+
+\subsection{Lagrangian Dynamics}
+
+\subsection{Hamiltonian Dynamics}
+
+\subsection{Legendre transformation}
+
+\subsection{examples}
+
+\section{Spunti}
+
+\subsection{Link to the Covariant Approach}
+
+\subsection{Open problems?}
+\begin{itemize}
+	\item We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+	\item We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match? \\
+		Yes! this is actually the result of \cite{forgeromero}. At pages 396-397 they show how to transgress the multisymplectic form to a symplectic form on Sol.\\
+		In theorem 4 pag 403 they show that this form coincide with the one by Peierls constructed a' la Dewitt.
+
+	\item there are other notion of moment map on the multisymplectic setting. For instance how the definition in section 4 of \cite{Gotay1998a} is related to the one in \cite{Ryvkin2018}?
+
+Marco ha fatto un'osservazione interessante: la densità hamiltoniana come definita da Forger-Romero non sembra a priori collegata a nessun elemento delle "L-infty algebra" usata nei suoi lavori.
+Questo e' in contrasto con il parallelismo che si vorrebbe fare tra algebra di poisson per i sistemi tipo di particella e L-infity algebra per i sistemi tipo campo.
+
+Anche Forger e Romero indicano come che uno dei grandi difetti del formalismo multi-simplettico il fatto che non sia chiaro quale sia la corretta struttura algebrica degli osservabili.
+Questo problema non è di poco conto visto che la maggior parte degli schemi di quantizzazione partono dal quantizzare l'algebra degli osservabili.
+
+Marco ha parlato con Gotay: dice che la forma ms per i campi è molto particolare (esatta e definita su un particolare fibrato) e che lo studio della geo multisymp a livello molto generale potrebbe alla fine non essere centrale o utile per quanto riguarda la meccanica.
+
+\end{itemize}
+
+%------------------------------------------------------------------------------------------------
+% Bibliography (BibTex)
+% https://arxiv.org/hypertex/bibstyles/
+%------------------------------------------------------------------------------------------------
+			\nocite{*}
+			\bibliographystyle{ieeetr}
+			\bibliography{biblio}
+%------------------------------------------------------------------------------------------------
 

### 2019-03-01 cps-via-ms.tex
small fix

--- 2017-06-16 cpsviams.tex
@@
 
-\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived from a multicanonical $m$-form $\theta$, obtained by pulling back the tautological $m$-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
+\item It turns out that  $\AffDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived from a multicanonical $m$-form $\theta$, obtained by pulling back the tautological $m$-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
 	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.

### 2019-03-01 ms-mechanics.tex
small fix

--- 2019-02-18 ms-mechanics.tex
@@
 	"Differential geometry and applications to modern physics" \\
+	%
+	\begin{minipage}[c]{0.5\textwidth}
+		\vspace{2em}
+		\centering
 		Department of Mathematics and Physics\\
@@
 		via Musei 41, 25121 Brescia, \underline{Italy}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[c]{0.5\textwidth}
+		\vspace{2em}
+		\centering
+		Department of Mathematics\\
+		KU Leuven\\
+		Celestijnenlaan 200B, 3001 Leuven, \underline{Belgium}
+	\end{minipage}
 }
 
-\documentclass[a4paper,12pt,fleqn]{scrartcl}  %Per La Stampa
-\usepackage[a4paper, margin=2cm]{geometry}
+\documentclass[a4paper,12pt,fleqn]{article}  %Per La Stampa
+\usepackage[a4paper, margin=3cm]{geometry}
 
@@
 \\
-As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g.
-a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium as a filament or a membrane).
+Just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g.
+a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (e.g.
+a continuous medium like a filament or a membrane).
 \\
-The aim of my talk is to give an account on the multisymplectic framework for (I-order) classical fields theories comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
+The aim of this talk is to give an account on the multisymplectic framework for (I-order) classical fields theories trying to comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
 \\
-Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.
+Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allows us to treat such formal object in a finite-dimensional setting.
 
@@
 
-\subsection{spunti Open problems}
-	We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+A questo punto si dovrebbe Essere chiaro il punto di partenza:
+\\
 
-	We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
+\section{Kinematics of Classical fields}
+The starting point is the \emph{configuration bundle} 
+ 	\begin{displaymath}
+ 		E = \left( \pi_{M,E} : E\rightarrow M \right)
+ 	\end{displaymath}
+is a smooth bundle encoding the kinematics.
 
-\section{Spunti dei Saggi}
-\subsection{Rogers: arXiv:1009.2975v3}
-Multisymplectic manifolds naturally arise in certain covariant Hamiltonian formalisms for classical field theory.
-In these formalisms, one describes a $(n+1)$-dimensional field theory by using a finite-dimensional $n$-plectic manifold as a \emph{multi-phase space} instead of an infinite-dimensional phase space. 
-The $n$-plectic form can be used to define a system of partial differential equations which are the analogue of Hamilton's equations in classical mechanics. 
-The solutions to these
-equations correspond to particular submanifolds of the multi-phase space that encode the value of the field at each point in space-time as well as the values of its time and spatial derivatives.
+\subsection{Jet Bundle}
+The first jet bundle of $E$ generalises the space of generalized velocities.
+
+The fiber over a point $y\in E$ is
+\begin{displaymath}
+	\left( J^1 E\right)_y = \left\lbrace \gamma \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ \gamma = \text{id}_{T_{\pi(x)} M} \right\rbrace
+\end{displaymath}
+(T = Tangent functor L = space of linear maps)
+
+which is and affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
+\begin{displaymath}
+	\vec{\left( J^1 E\right)_y} = \left\lbrace z \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ z = 0 \right\rbrace
+	\cong text{L}(T_{\pi(y)}M, T_y E)
+\end{displaymath}
+
+\section{Spunti / Open problems}
+\begin{itemize}
+	\item We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
+	\item We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
+	\item there are other notion of moment map on the multisymplectic setting. For instance how the definition in section 4 of \cite{Gotay1998a} is related to the one in \cite{Ryvkin2018}?
+\end{itemize}
+
+\nocite{*}
+\bibliographystyle{alpha}
+\bibliography{biblio}
 

### 2019-03-01 ms-mechanics.tex

--- 2019-03-01 ms-mechanics.tex
@@
 		via Musei 41, 25121 Brescia, \underline{Italy}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[c]{0.5\textwidth}
+		\vspace{2em}
+		\centering
+		Department of Mathematics\\
+		KU Leuven\\
+		Celestijnenlaan 200B, 3001 Leuven, \underline{Belgium}
+	\end{minipage}
 }
@@
 \\
-As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g.
-a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium like a filament or a membrane).
+Just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g.
+a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (e.g.
+a continuous medium like a filament or a membrane).
 \\
-The aim of my talk is to give an account on the multisymplectic framework for (I-order) classical fields theories comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
+The aim of this talk is to give an account on the multisymplectic framework for (I-order) classical fields theories trying to comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
 \\
-Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.
+Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allows us to treat such formal object in a finite-dimensional setting.
 

### 2019-03-11 ms-mechanics.tex
note on ms mech.

--- 2019-03-01 ms-mechanics.tex
@@
 	"Differential geometry and applications to modern physics" \\
-	%
-	\begin{minipage}[c]{0.5\textwidth}
-		\vspace{2em}
-		\centering
 	Department of Mathematics and Physics\\
@@
 	via Musei 41, 25121 Brescia, \underline{Italy}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[c]{0.5\textwidth}
-		\vspace{2em}
-		\centering
-		Department of Mathematics\\
-		KU Leuven\\
-		Celestijnenlaan 200B, 3001 Leuven, \underline{Belgium}
-	\end{minipage}
 }
 
-\documentclass[a4paper,12pt,fleqn]{article}  %Per La Stampa
-\usepackage[a4paper, margin=3cm]{geometry}
+\documentclass[a4paper,12pt,fleqn]{scrartcl}  %Per La Stampa
+\usepackage[a4paper, margin=2cm]{geometry}
 
 \usepackage{amsmath}
-\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
+\usepackage{amsfonts}
+%\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
 \usepackage[subpreambles=true]{standalone}
@@
 
-\providecommand{\oast}{\ensuremath{\:\!%
- {\raisebox{0.1ex}{$\scriptscriptstyle \bigcirc$} \hspace{-0.5em} \ast}}}
-\providecommand{\ostar}{\ensuremath{\:\!%
- {\raisebox{0.05ex}{$\scriptscriptstyle \bigcirc$} \hspace{-0.5em} \star}}}
-\providecommand{\smoast}{\ensuremath{%
- {\raisebox{-0.25ex}{$\textstyle \circ$} \hspace{-0.42em}
- {\scriptscriptstyle \ast}}}}
-\providecommand{\smostar}{\ensuremath{%
- {\raisebox{-0.25ex}{$\textstyle \circ$} \hspace{-0.42em}
-  \raisebox{0.05ex}{$\scriptscriptstyle \star$}}}}
-
 \begin{document}
 \maketitle
-
-$$
-\ast 
-\star 
-\oast 
-\ostar
-\smoast
-\smostar
-J^\smostar
-J^\smoast
-J^\ostar
-$$
 
@@
 \\
-Just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g.
-a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (e.g.
-a continuous medium like a filament or a membrane).
+As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g.
+a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium as a filament or a membrane).
 \\
-The aim of this talk is to give an account on the multisymplectic framework for (I-order) classical fields theories trying to comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
+The aim of my talk is to give an account on the multisymplectic framework for (I-order) classical fields theories comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
 \\
-Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allows us to treat such formal object in a finite-dimensional setting.
+Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.
 
@@
 
-\section{A glance at the geometric approach to classical mechanics}
-Recall: Geometric Mechanics of Classical system
-Configuration space
-Generalized velocities space and phase space
-...
-
-\section{Far capire cosa intendo per campo classico}
+\subsection{Far capire cosa intendo per campo classico}
 Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
@@
 
-A questo punto si dovrebbe Essere chiaro il punto di partenza:
-\\
+\subsection{spunti Open problems}
+	We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
 
-\section{Kinematics of Classical fields}
-The starting point is the \emph{configuration bundle} 
- 	\begin{displaymath}
- 		E = \left( \pi_{M,E} : E\rightarrow M \right)
- 	\end{displaymath}
-is a smooth bundle encoding the kinematics.
+	We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
 
-\subsection{Jet Bundle}
-The first jet bundle of $E$ generalises the space of generalized velocities.
-
-The fiber over a point $y\in E$ is
-\begin{displaymath}
-	\left( J^1 E\right)_y = \left\lbrace \gamma \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ \gamma = \text{id}_{T_{\pi(x)} M} \right\rbrace
-\end{displaymath}
-(T = Tangent functor L = space of linear maps)
-
-which is and affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
-\begin{displaymath}
-	\vec{\left( J^1 E\right)_y} = \left\lbrace z \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ z = 0 \right\rbrace
-	\cong text{L}(T_{\pi(y)}M, T_y E)
-\end{displaymath}
-
-\section{Spunti / Open problems}
-\begin{itemize}
-	\item We have a momap on ms mfd and a momap on mapping space (as diffeological space) does the two match?
-	\item We have a canonical m-s structure on J.. and a canonical poisson structure con cov phase space (Peierls bracket) does the two match?
-	\item there are other notion of moment map on the multisymplectic setting. For instance how the definition in section 4 of \cite{Gotay1998a} is related to the one in \cite{Ryvkin2018}?
-\end{itemize}
-
-\nocite{*}
-\bibliographystyle{alpha}
-\bibliography{biblio}
+\section{Spunti dei Saggi}
+\subsection{Rogers: arXiv:1009.2975v3}
+Multisymplectic manifolds naturally arise in certain covariant Hamiltonian formalisms for classical field theory.
+In these formalisms, one describes a $(n+1)$-dimensional field theory by using a finite-dimensional $n$-plectic manifold as a \emph{multi-phase space} instead of an infinite-dimensional phase space. 
+The $n$-plectic form can be used to define a system of partial differential equations which are the analogue of Hamilton's equations in classical mechanics. 
+The solutions to these
+equations correspond to particular submanifolds of the multi-phase space that encode the value of the field at each point in space-time as well as the values of its time and spatial derivatives.
 

### 2019-03-11 cps-via-ms.tex

@@
 \begin{abstract}
-In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
+In this short talk we present part of the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
 In particular we focus our attention on the construction of the \emph{Covariant Phase Space}, starting from the multi-symplectic approach to geometric classic field theories.

### 2019-03-29 ms-mechanics.tex
Tiny update in ms-mechanics notes

--- 2019-03-01 ms-mechanics.tex
@@
 \usepackage{amsmath}
-\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
+\usepackage{amsfonts}
+%\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
 \usepackage[subpreambles=true]{standalone}
@@
 \usepackage{hyperref}
-
-%\usepackage{Latex-Theorem/theoremtemplate}
-
-%	\renewcommand{\AffDualJet}{ J^{1 \TwistedAffine}E }
-%	\renewcommand{\LinDualJet}{ \overrightarrow{J^{1 \TwistedLinear}E} }
+\usepackage{tabularx}
 
@@
 J^\smoast
-J^\ostar
+%J^\ostar
 $$
@@
 Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
-\begin{table}[]
-\begin{tabular}{lll}
-	System & Configuration space (locally) & protoype 
- 	\\
-	Ordinary system & $\mathbb{R}^n$ with $n\in \mathbb{N} = Hom_{set}(\{1,\ldots n\}, \mathbb{R})$ & A point on a $n$-dimensional mfd.
-	\\
-	1 dimensional field & $\mathbb{R}^\mathbb{R} = C^\infty(\mathbb{R},\mathbb{R})$ & collection of points on a line each one parametrized by ...
-	\\
-	n dimensional field & $(\mathbb{R}^m)^{\mathbb{R}^n} = C^\infty (\mathbb{R}^n, \mathbb{R}^m)$ & ...
-\end{tabular}
-\end{table}
+
+\begin{tabularx}{\textwidth}{c X c c}
+	System & Prototype & DoF & Configuration space (locally)\\
+	Ordinary classical mech system & point-particle on a  $q$-dim manifold &
+	$q$ finite (discrete) & $\mathbb{R}^n = Hom_{set}(\{1,\ldots n\}, \mathbb{R})$ \\
+	1-dim. field & collection of points on a line each one parametrized by a point on the manifold $Q$ & $q$ for each point on the continuous line (infinite and continuous) &
+	...
+%	\\
+%	n dimensional field & $(\mathbb{R}^m)^{\mathbb{R}^n} = C^\infty (\mathbb{R}^n, \mathbb{R}^m)$ & ...
+\end{tabularx}
 

### 2019-04-10 ms-mechanics.tex
texing note of my talk..

@@
 \usepackage{tabularx}
+
+\usepackage{Latex-Theorem/theoremtemplate}
 
@@
 
-\subsection{Configuration Bundle}
--Kinematics of Classical fields-
-The starting point is the \emph{configuration bundle} 
+\subsection{From the configuration Space to the configuration Bundle}
+Recall that a physical field has to be thought as the assignment of a quantity to every point of a base manifold (a "spacetime" most of the time).
+\\
+It is reasonable that the object needed to encode the kinematics of our field system ougth to be a smooth bundle, that would be the proper language in order to formulate the notion of smooth physical quantity.
+\\
+\begin{definition}[Configuration bundle] 
  	\begin{displaymath}
@@
  	\end{displaymath}
-is a smooth bundle encoding the kinematics.
+Smooth fiber bundle $E\sim(x^\mu,q^A)$ with typical fiber $Q\sim(q^A)$ over a smooth, oriented and connected base manifold $M\sim(x^\mu)$.
+\end{definition}
+This definition may seem a bit too bare, but has to be kept in mind that we are describing a structure suitable for many different models.
+\\
+The collection $\Gamma(E)$ of all smooth sections has to be understood as the set of kinematics configurations of the system and the typical fiber $Q$ can be tought as the configuration space of possible values of the field in a fixed point.
 
-\subsection{Jet Bundle}
-The first jet bundle of $E$ generalises the space of generalized velocities.
+\subsection{From the space of generalized velocities to the I Jet bundle}
+The collection of all field configurations together with their partial derivatives up to $r$-th order can be represented by the space of the sections of the $r$-th jet bundle.
+\\
+In what follows we shall only need the first order Jet bundle.
+This restriction reflect the fact that almost all known examples of field theories are governed by second order PDE and derived from Lagrangian depending only on first order partial derivative.
+Also, it is also reasonable to develop the theory starting from this point directly extending the ordinary geometric mechanics theory.
 
-The fiber over a point $y\in E$ is
+\begin{definition}[I Jet bundle]
+Affine bundle $J^1 E \rightarrow E$, with fibers over a point $y\in E$ given by
 \begin{displaymath}
@@
 \end{displaymath}
-(T = Tangent functor L = space of linear maps)
-
-which is and affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
+where $T$ is the tangent functor, $L$ is the space of linear maps and $\pi$ is the bundle projection of $E$ over $M$.
+\\
+This fiber is an affine subspace of $\text{L}(T_{\pi(y)}M, T_y E)$ modelled on the following (difference) vector space:
 \begin{displaymath}
 	\vec{\left( J^1 E\right)_y} = \left\lbrace z \in \text{L}(T_{\pi(y)}M, T_y E) \; \vert \: T\pi \circ z = 0 \right\rbrace
-	\cong text{L}(T_{\pi(y)}M, T_y E)
+	\cong \text{L}(T_{\pi(y)}M, T_y E)
+	\cong T_x^\ast M \otimes V_y E
 \end{displaymath}
+\end{definition}
 
